---
title: 'First look at interpretators: Replacement of nominal by verbal types'
output:
  pdf_document: default
  html_document: default
---

```{r}
library(tidyverse)
library(effects)
library(lattice)
library(latticeExtra)
library(vcd)
library(car)
library(arm)

source("./r_utils/my_utils.R")

all_data <- read.csv("./data/all_data.csv", stringsAsFactors = T)

contrasts(all_data$variety) <- contr.sum(2)
```


# Data
```{r}
all_data_replacement <- subset(all_data, interpretator_type != "none")
all_data_replacement$interpretator_verbal <- as.integer(ifelse(all_data_replacement$interpretator_type == "verbal", 1, 0))
all_data_replacement <- droplevels(all_data_replacement)
contrasts(all_data_replacement$variety) <- contr.sum(2)
```


# List of interpretators

- Interpretators ordered by overall occurrence rate
- Broken down by verb and (major) period

```{r}
# List of interpretators
all_data_replacement$interpretator_ordered <- all_data_replacement$interpretator
all_data_replacement$interpretator_ordered <- factor(
  all_data_replacement$interpretator_ordered,
  levels=names(sort(table(all_data_replacement$interpretator), decreasing=T)),
  ordered=T
)
structable(verb + year_bins_100 ~ interpretator_ordered, all_data_replacement)
```



# Deceive

## Data
```{r}
data_long_deceive_replacement <- subset(all_data_replacement, verb == "deceive" & macro_genre == "fiction")
rownames(data_long_deceive_replacement) <- 1:nrow(data_long_deceive_replacement)
```

## Data inspection

```{r}
structable(variety ~ year_bins_40, data_long_deceive_replacement, subset=macro_genre == "fiction")
```
```{r fig.height=3, fig.width=4.5}
data_long_deceive_replacement %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=4) +
  facet_grid(rows=vars(variety)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") +
  labs(title="Deceive",
       subtitle="Cases with interpretators, by Year and Variety (Fiction)")
```


## Model

```{r}
m_long_deceive_replacement <- glm(
  interpretator_verbal ~ year_c + variety, 
  data=data_long_deceive_replacement, family="binomial")

display(m_long_deceive_replacement)
```


## Model checking

Residual plots
```{r fig.height=2.5, fig.width=6}
residualPlots(m_long_deceive_replacement, layout=c(1,3), tests = F, ask=F)
```

Marginal model plots
```{r fig.height=3, fig.width=5, warning=F}
marginalModelPlots(m_long_deceive_replacement, layout=c(1,2))
```

Influence diagnostics
```{r fig.height=4, fig.width=4}
outlier_id <- influencePlot(m_long_deceive_replacement)
```

Effect of influential cases on coefficients + SEs
```{r}
outlier_id <- as.integer(rownames(outlier_id))

m_long_deceive_replacement_1 <- update(m_long_deceive_replacement, subset=-outlier_id[1])
m_long_deceive_replacement_2 <- update(m_long_deceive_replacement, subset=-outlier_id[2])
m_long_deceive_replacement_3 <- update(m_long_deceive_replacement, subset=-outlier_id[3])
m_long_deceive_replacement_4 <- update(m_long_deceive_replacement, subset=-outlier_id[4])
m_long_deceive_replacement_5 <- update(m_long_deceive_replacement, subset=-outlier_id[5])
m_long_deceive_replacement_all <- update(m_long_deceive_replacement, subset=-outlier_id)

coef_change <- compareCoefs(
  m_long_deceive_replacement, 
  m_long_deceive_replacement_1,
  m_long_deceive_replacement_2, 
  m_long_deceive_replacement_3,
  m_long_deceive_replacement_4,
  m_long_deceive_replacement_5,
  m_long_deceive_replacement_all, digits=2)
```

```{r fig.height=2, fig.width=4}
plot1 <- xyplot(as.numeric(coef_change[4,]) ~ 1:length(coef_change[4,]),
       scales=list(x=list(at=1:7,labels=1:7)),
       par.settings=my_settings, axis=axis_L, ylim=c(-.1,2.1), pch=19,
       xlab.top="Year (95% CI)",
       xlab="", ylab="",
       panel=function(x,y,...){
         panel.xyplot(x,y,...)
         panel.abline(h=0, col="grey")
         panel.arrows(x0=x, x1=x, 
                      y0=y-2*as.numeric(coef_change[5,]), 
                      y1=y+2*as.numeric(coef_change[5,]),
                      code=3, angle=90, length=.03)
       })
plot2 <- xyplot(as.numeric(coef_change[7,]) ~ 1:length(coef_change[7,]),
       scales=list(x=list(at=1:7,labels=1:7)),
       par.settings=my_settings, axis=axis_L, ylim=c(-1,.1), pch=19,
       xlab.top="Variety (95% CI)",
       xlab="", ylab="",
       panel=function(x,y,...){
         panel.xyplot(x,y,...)
         panel.abline(h=0, col="grey")
         panel.arrows(x0=x, x1=x, 
                      y0=y-2*as.numeric(coef_change[8,]), 
                      y1=y+2*as.numeric(coef_change[8,]),
                      code=3, angle=90, length=.03)
       })
cowplot::plot_grid(plot1, plot2)
```
```{r}
data_long_deceive_replacement[outlier_id,]
```



## Model visualization

```{r fig.width=6, fig.height=3}
plot(effects::predictorEffect(
  "year_c",
  m_long_deceive_replacement, 
  confidence.level=.95), 
  axes=list(y=list(type="response", lim=c(0,1))),
  lattice=list(array=list(row=1, col=1, nrow=1, ncol=2, more=T)),
  main="Year", xlab="")

plot(effects::predictorEffect(
  "variety",
  m_long_deceive_replacement, 
  confidence.level=.95), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=2, nrow=1, ncol=2, more=F)),
  main="Variety", xlab="", ylab="")

```

```{r}
deceive_replacement_effect_year_AmE <- effect(
  "year_c",  m_long_deceive_replacement, confidence.level=.95,
  xlevels=list(
    year_c=seq(min(subset(data_long_deceive_replacement, variety=="AmE")$year_c), 
               max(subset(data_long_deceive_replacement, variety=="AmE")$year_c), 
               length.out=50)),
  fixed.predictors=list(given.values=c(
    variety1=1)))

deceive_replacement_effect_year_BrE <- effect(
  "year_c",  m_long_deceive_replacement, confidence.level=.95,
  xlevels=list(
    year_c=seq(min(subset(data_long_deceive_replacement, variety=="BrE")$year_c), 
               max(subset(data_long_deceive_replacement, variety=="BrE")$year_c), 
               length.out=50)),
  fixed.predictors=list(given.values=c(
    variety1=-1)))

deceive_replacement_effect_variety <- effect(
  "variety",  m_long_deceive_replacement, confidence.level=.95,
  fixed.predictors=list(given.values=c(
    year_c=-as.numeric(coef(m_long_deceive_replacement)[1]/coef(m_long_deceive_replacement)[2]))))
```

```{r}
data_long_deceive_replacement_BrE <- subset(
  data_long_deceive_replacement, variety=="BrE")

data_long_deceive_replacement_AmE <- subset(
  data_long_deceive_replacement, variety=="AmE")
```


```{r fig.height=3.3, fig.width=3.3}
x_breaks_AmE = seq(min(data_long_deceive_replacement_AmE$year_c), 
               max(data_long_deceive_replacement_AmE$year_c), length.out=5)
x_breaks_BrE = seq(min(data_long_deceive_replacement_BrE$year_c), 
               max(data_long_deceive_replacement_BrE$year_c), length.out=5)

plot1 <- xyplot(
  1~1, type="n", xlim=c(-6,.5), ylim=c(0,1),
  ylab="Verbal interpretators (%)", xlab="",
  par.settings=my_settings, axis=axis_all,
  scales=list(x=list(at=c(-6,-4,-2, 0), label=c(1700, 1800, 1900, 2000)),
              y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
  panel=function(x,y){
    panel.polygon(y=plogis(c(deceive_replacement_effect_year_AmE$lower, rev(deceive_replacement_effect_year_AmE$upper))),
                  x=c(deceive_replacement_effect_year_AmE$x$year_c, rev(deceive_replacement_effect_year_AmE$x$year_c)),
                  border=F, col="steelblue3", alpha=.3)
    
    panel.polygon(y=plogis(c(deceive_replacement_effect_year_BrE$lower, rev(deceive_replacement_effect_year_BrE$upper))),
                  x=c(deceive_replacement_effect_year_BrE$x$year_c, rev(deceive_replacement_effect_year_BrE$x$year_c)),
                  border=F, col="tomato3", alpha=.3)
    
    
    panel.points(y=plogis(deceive_replacement_effect_year_AmE$fit), x=deceive_replacement_effect_year_AmE$x$year_c, type="l", col="steelblue3")
    panel.points(y=plogis(deceive_replacement_effect_year_BrE$fit), x=deceive_replacement_effect_year_BrE$x$year_c, type="l", col="tomato3")
    
    panel.dotdiagram(subset(data_long_deceive_replacement_AmE, interpretator_verbal==1)$year_c, 
                     y_anchor = 1.22, 
                     seq_min=-6, seq_max=.5, n_bins = 90, scale_y = .015, downwards = F,
                     set_cex=.3, set_pch=19, set_col = "steelblue3")
    
    panel.dotdiagram(subset(data_long_deceive_replacement_AmE, interpretator_verbal==0)$year_c, 
                     y_anchor = 1.22, 
                     seq_min=-6, seq_max=.5, n_bins = 90, scale_y = .015, downwards = T,
                     set_cex=.3, set_pch=1, set_col = "steelblue3")

    panel.dotdiagram(subset(data_long_deceive_replacement_BrE, interpretator_verbal==1)$year_c, 
                     y_anchor = 1.45, 
                     seq_min=-6, seq_max=.5, n_bins = 90, scale_y = .015, downwards = F,
                     set_cex=.3, set_pch=19, set_col = "tomato3")
    
    panel.dotdiagram(subset(data_long_deceive_replacement_BrE, interpretator_verbal==0)$year_c, 
                     y_anchor = 1.45, 
                     seq_min=-6, seq_max=.5, n_bins = 90, scale_y = .015, downwards = T,
                     set_cex=.3, set_pch=1, set_col = "tomato3")
    
    panel.points(y=tapply(data_long_deceive_replacement_AmE$interpretator_verbal, 
                          cut(data_long_deceive_replacement_AmE$year_c, 
                              breaks = x_breaks_AmE), mean),
                 x=(x_breaks_AmE[1:4] + x_breaks_AmE[2:5])/2, col="steelblue3", type="l",
                 lty=3, alpha=.5, lwd=1, lineend="square")
    
    panel.points(y=tapply(data_long_deceive_replacement_AmE$interpretator_verbal, 
                          cut(data_long_deceive_replacement_AmE$year_c, 
                              breaks = x_breaks_AmE), mean),
                 x=(x_breaks_AmE[1:4] + x_breaks_AmE[2:5])/2, pch=21, col="steelblue3", 
                 cex=.3, alpha=.5)
    
    
    panel.points(y=tapply(data_long_deceive_replacement_BrE$interpretator_verbal, 
                          cut(data_long_deceive_replacement_BrE$year_c, 
                              breaks = x_breaks_BrE), mean),
                 x=(x_breaks_BrE[1:4] + x_breaks_BrE[2:5])/2, col="tomato3", type="l",
                 lty=3, alpha=.5, lwd=1, lineend="square")
    
    panel.points(y=tapply(data_long_deceive_replacement_BrE$interpretator_verbal, 
                          cut(data_long_deceive_replacement_BrE$year_c, 
                              breaks = x_breaks_BrE), mean),
                 x=(x_breaks_BrE[1:4] + x_breaks_BrE[2:5])/2, pch=21, col="tomato3", 
                 cex=.3, alpha=.5)
    
    panel.text(x=.8, y=c(1.22, 1.45), label=c("AmE", "BrE"), adj=0, cex=.8,
               col=c("steelblue3", "tomato3"))    
        
    panel.segments(x0=-6, x1=.5, y0=c(1.22, 1.45), y1=c(1.22, 1.45), lwd=.5, col="grey40")
    panel.text(x=-6, y=c(1.18, 1.26), label=c("nominal", "verbal"), adj=0, cex=.6, col="grey40")
    panel.text(x=-5.8, y=.93, label="deceive", font=3, adj=0)
    })


print(plot1, position=c(0,0,.89,.7))

cairo_pdf("./figures/deceive_replacement.pdf", width=3.3, height=3.3)
print(plot1, position=c(0,0,.89,.7))
dev.off()
```



# Delude

## Data

```{r}
data_long_delude_replacement <- subset(all_data_replacement, verb == "delude" & macro_genre == "fiction")
rownames(data_long_delude_replacement) <- 1:nrow(data_long_delude_replacement)
```


## Data inspection

```{r}
structable(variety ~ year_bins_40, data_long_delude_replacement, subset=macro_genre == "fiction")
```

```{r fig.height=3, fig.width=4.5}
data_long_delude_replacement %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=4) +
  facet_grid(rows=vars(variety)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") +
  labs(title="Delude",
       subtitle="Cases with interpretators, by Year and Variety (Fiction)")
```

## Model
```{r}
m_long_delude_replacement <- glm(
  interpretator_verbal ~ year_c + variety, 
  data=data_long_delude_replacement, family="binomial")

display(m_long_delude_replacement)
```

## Model checking

Residual plots
```{r fig.height=2.5, fig.width=6}
residualPlots(m_long_delude_replacement, layout=c(1,3), tests = F, ask=F)
```

Marginal model plots
```{r fig.height=3, fig.width=5, warning=F}
marginalModelPlots(m_long_delude_replacement, layout=c(1,2))
```

Influence diagnostics
```{r fig.height=4, fig.width=4}
outlier_id <- influencePlot(m_long_delude_replacement)
```

Effect of influential cases on coefficients + SEs
```{r}
outlier_id <- as.integer(rownames(outlier_id))

m_long_delude_replacement_1 <- update(m_long_delude_replacement, subset=-outlier_id[1])
m_long_delude_replacement_2 <- update(m_long_delude_replacement, subset=-outlier_id[2])
m_long_delude_replacement_3 <- update(m_long_delude_replacement, subset=-outlier_id[3])
m_long_delude_replacement_4 <- update(m_long_delude_replacement, subset=-outlier_id[4])
m_long_delude_replacement_all <- update(m_long_delude_replacement, subset=-outlier_id)

coef_change <- compareCoefs(
  m_long_delude_replacement, 
  m_long_delude_replacement_1,
  m_long_delude_replacement_2, 
  m_long_delude_replacement_3,
  m_long_delude_replacement_4,
  m_long_delude_replacement_all, digits=2)
```
```{r fig.height=2, fig.width=4}
plot1 <- xyplot(as.numeric(coef_change[4,]) ~ 1:length(coef_change[4,]),
       scales=list(x=list(at=1:7,labels=1:7)),
       par.settings=my_settings, axis=axis_L, ylim=c(-.1,2.6), pch=19,
       xlab.top="Year (95% CI)",
       xlab="", ylab="",
       panel=function(x,y,...){
         panel.xyplot(x,y,...)
         panel.abline(h=0, col="grey")
         panel.arrows(x0=x, x1=x, 
                      y0=y-2*as.numeric(coef_change[5,]), 
                      y1=y+2*as.numeric(coef_change[5,]),
                      code=3, angle=90, length=.03)
       })
plot2 <- xyplot(as.numeric(coef_change[7,]) ~ 1:length(coef_change[7,]),
       scales=list(x=list(at=1:7,labels=1:7)),
       par.settings=my_settings, axis=axis_L, ylim=c(-1.3,1), pch=19,
       xlab.top="Variety (95% CI)",
       xlab="", ylab="",
       panel=function(x,y,...){
         panel.xyplot(x,y,...)
         panel.abline(h=0, col="grey")
         panel.arrows(x0=x, x1=x, 
                      y0=y-2*as.numeric(coef_change[8,]), 
                      y1=y+2*as.numeric(coef_change[8,]),
                      code=3, angle=90, length=.03)
       })
cowplot::plot_grid(plot1, plot2)
```

```{r}
data_long_delude_replacement[outlier_id,]
```

## Model visualization

```{r fig.width=6, fig.height=3}
plot(effects::predictorEffect(
  "year_c",
  m_long_delude_replacement, 
  confidence.level=.95), 
  axes=list(y=list(type="response", lim=c(0,1))),
  lattice=list(array=list(row=1, col=1, nrow=1, ncol=2, more=T)),
  main="Year", xlab="")

plot(effects::predictorEffect(
  "variety",
  m_long_delude_replacement, 
  confidence.level=.95), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=2, nrow=1, ncol=2, more=F)),
  main="Variety", xlab="", ylab="")

```

```{r}
delude_replacement_effect_year_AmE <- effect(
  "year_c",  m_long_delude_replacement, confidence.level=.95,
  xlevels=list(
    year_c=seq(min(subset(data_long_delude_replacement, variety=="AmE")$year_c), 
               max(subset(data_long_delude_replacement, variety=="AmE")$year_c), 
               length.out=50)),
  fixed.predictors=list(given.values=c(
    variety1=1)))

delude_replacement_effect_year_BrE <- effect(
  "year_c",  m_long_delude_replacement, confidence.level=.95,
  xlevels=list(
    year_c=seq(min(subset(data_long_delude_replacement, variety=="BrE")$year_c), 
               max(subset(data_long_delude_replacement, variety=="BrE")$year_c), 
               length.out=50)),
  fixed.predictors=list(given.values=c(
    variety1=-1)))

delude_replacement_effect_variety <- effect(
  "variety",  m_long_delude_replacement, confidence.level=.95,
  fixed.predictors=list(given.values=c(
    year_c=-as.numeric(coef(m_long_delude_replacement)[1]/coef(m_long_delude_replacement)[2]))))
```

```{r}
data_long_delude_replacement_BrE <- subset(
  data_long_delude_replacement, variety=="BrE")

data_long_delude_replacement_AmE <- subset(
  data_long_delude_replacement, variety=="AmE")
```


```{r fig.height=3.3, fig.width=3.3}
x_breaks_AmE = seq(min(data_long_delude_replacement_AmE$year_c), 
               max(data_long_delude_replacement_AmE$year_c), length.out=5)
x_breaks_BrE = seq(min(data_long_delude_replacement_BrE$year_c), 
               max(data_long_delude_replacement_BrE$year_c), length.out=5)

plot1 <- xyplot(
  1~1, type="n", xlim=c(-6,.5), ylim=c(0,1),
  ylab="Verbal interpretators (%)", xlab="",
  par.settings=my_settings, axis=axis_all,
  scales=list(x=list(at=c(-6,-4,-2, 0), label=c(1700, 1800, 1900, 2000)),
              y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
  panel=function(x,y){
    panel.polygon(y=plogis(c(delude_replacement_effect_year_AmE$lower, rev(delude_replacement_effect_year_AmE$upper))),
                  x=c(delude_replacement_effect_year_AmE$x$year_c, rev(delude_replacement_effect_year_AmE$x$year_c)),
                  border=F, col="steelblue3", alpha=.3)
    
    panel.polygon(y=plogis(c(delude_replacement_effect_year_BrE$lower, rev(delude_replacement_effect_year_BrE$upper))),
                  x=c(delude_replacement_effect_year_BrE$x$year_c, rev(delude_replacement_effect_year_BrE$x$year_c)),
                  border=F, col="tomato3", alpha=.3)
    
    
    panel.points(y=plogis(delude_replacement_effect_year_AmE$fit), x=delude_replacement_effect_year_AmE$x$year_c, type="l", col="steelblue3")
    panel.points(y=plogis(delude_replacement_effect_year_BrE$fit), x=delude_replacement_effect_year_BrE$x$year_c, type="l", col="tomato3")
    
    panel.dotdiagram(subset(data_long_delude_replacement_AmE, interpretator_verbal==1)$year_c, 
                     y_anchor = 1.22, 
                     seq_min=-6, seq_max=.5, n_bins = 90, scale_y = .015, downwards = F,
                     set_cex=.3, set_pch=19, set_col = "steelblue3")
    
    panel.dotdiagram(subset(data_long_delude_replacement_AmE, interpretator_verbal==0)$year_c, 
                     y_anchor = 1.22, 
                     seq_min=-6, seq_max=.5, n_bins = 90, scale_y = .015, downwards = T,
                     set_cex=.3, set_pch=1, set_col = "steelblue3")

    panel.dotdiagram(subset(data_long_delude_replacement_BrE, interpretator_verbal==1)$year_c, 
                     y_anchor = 1.45, 
                     seq_min=-6, seq_max=.5, n_bins = 90, scale_y = .015, downwards = F,
                     set_cex=.3, set_pch=19, set_col = "tomato3")
    
    panel.dotdiagram(subset(data_long_delude_replacement_BrE, interpretator_verbal==0)$year_c, 
                     y_anchor = 1.45, 
                     seq_min=-6, seq_max=.5, n_bins = 90, scale_y = .015, downwards = T,
                     set_cex=.3, set_pch=1, set_col = "tomato3")
    
    panel.points(y=tapply(data_long_delude_replacement_AmE$interpretator_verbal, 
                          cut(data_long_delude_replacement_AmE$year_c, 
                              breaks = x_breaks_AmE), mean),
                 x=(x_breaks_AmE[1:4] + x_breaks_AmE[2:5])/2, col="steelblue3", type="l",
                 lty=3, alpha=.5, lwd=1, lineend="square")
    
    panel.points(y=tapply(data_long_delude_replacement_AmE$interpretator_verbal, 
                          cut(data_long_delude_replacement_AmE$year_c, 
                              breaks = x_breaks_AmE), mean),
                 x=(x_breaks_AmE[1:4] + x_breaks_AmE[2:5])/2, pch=21, col="steelblue3", 
                 cex=.3, alpha=.5)
    
    
    panel.points(y=tapply(data_long_delude_replacement_BrE$interpretator_verbal, 
                          cut(data_long_delude_replacement_BrE$year_c, 
                              breaks = x_breaks_BrE), mean),
                 x=(x_breaks_BrE[1:4] + x_breaks_BrE[2:5])/2, col="tomato3", type="l",
                 lty=3, alpha=.5, lwd=1, lineend="square")
    
    panel.points(y=tapply(data_long_delude_replacement_BrE$interpretator_verbal, 
                          cut(data_long_delude_replacement_BrE$year_c, 
                              breaks = x_breaks_BrE), mean),
                 x=(x_breaks_BrE[1:4] + x_breaks_BrE[2:5])/2, pch=21, col="tomato3", 
                 cex=.3, alpha=.5)
    
    panel.text(x=.8, y=c(1.22, 1.45), label=c("AmE", "BrE"), adj=0, cex=.8,
               col=c("steelblue3", "tomato3"))
    
    panel.segments(x0=-6, x1=.5, y0=c(1.22, 1.45), y1=c(1.22, 1.45), lwd=.5, col="grey40")
    panel.text(x=-6, y=c(1.18, 1.26), label=c("nominal", "verbal"), adj=0, cex=.6, col="grey40")
    panel.text(x=-5.8, y=.93, label="delude", font=3, adj=0)
    })


print(plot1, position=c(0,0,.89,.7))

cairo_pdf("./figures/delude_replacement.pdf", width=3.3, height=3.3)
print(plot1, position=c(0,0,.89,.7))
dev.off()
```




# Fool

## Data
```{r}
data_long_fool_replacement <- subset(all_data_replacement, verb == "fool" & macro_genre == "fiction")
rownames(data_long_fool_replacement) <- 1:nrow(data_long_fool_replacement)
```


## Data inspection

```{r}
structable(variety ~ year_bins_40, data_long_fool_replacement, subset=macro_genre == "fiction")
```

```{r fig.height=3, fig.width=4.5}
data_long_fool_replacement %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=2) +
  facet_grid(rows=vars(variety)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") +
  labs(title="Fool",
       subtitle="Cases with interpretators, by Year and Variety (Fiction)")
```


## Model
```{r}
m_long_fool_replacement <- glm(
  interpretator_verbal ~ year_c, 
  data=data_long_fool_replacement, 
  subset=variety=="AmE", family="binomial")

display(m_long_fool_replacement)
```

## Model checking

Residual plots
```{r fig.height=2.5, fig.width=6}
residualPlots(m_long_fool_replacement, layout=c(1,3), tests = F, ask=F)
```

Marginal model plots
```{r fig.height=3, fig.width=5, warning=F}
marginalModelPlots(m_long_fool_replacement, layout=c(1,2))
```

Influence diagnostics
```{r fig.height=4, fig.width=4}
outlier_id <- influencePlot(m_long_fool_replacement)
```

Effect of influential cases on coefficients + SEs
```{r}
outlier_id <- as.integer(rownames(outlier_id))

m_long_fool_replacement_1 <- update(m_long_fool_replacement, subset=-outlier_id[1])
m_long_fool_replacement_2 <- update(m_long_fool_replacement, subset=-outlier_id[2])
m_long_fool_replacement_3 <- update(m_long_fool_replacement, subset=-outlier_id[3])
m_long_fool_replacement_4 <- update(m_long_fool_replacement, subset=-outlier_id[4])
m_long_fool_replacement_all <- update(m_long_fool_replacement, subset=-outlier_id)

coef_change <- compareCoefs(
  m_long_fool_replacement, 
  m_long_fool_replacement_1,
  m_long_fool_replacement_2, 
  m_long_fool_replacement_3,
  m_long_fool_replacement_4,
  m_long_fool_replacement_all, digits=2)
```

```{r fig.height=2, fig.width=2}
xyplot(as.numeric(coef_change[4,]) ~ 1:length(coef_change[4,]),
       scales=list(x=list(at=1:6,labels=1:6)),
       par.settings=my_settings, axis=axis_L, ylim=c(-.1,5), pch=19,
       xlab.top="Year (95% CI)",
       xlab="", ylab="",
       panel=function(x,y,...){
         panel.xyplot(x,y,...)
         panel.abline(h=0, col="grey")
         panel.arrows(x0=x, x1=x, 
                      y0=y-2*as.numeric(coef_change[5,]), 
                      y1=y+2*as.numeric(coef_change[5,]),
                      code=3, angle=90, length=.03)
       })
```

```{r}
data_long_fool_replacement[outlier_id,]
```


## Model visualization

```{r fig.width=6, fig.height=3}
plot(effects::predictorEffect(
  "year_c",
  m_long_fool_replacement, 
  confidence.level=.95), 
  axes=list(y=list(type="response", lim=c(0,1))),
  lattice=list(array=list(row=1, col=1, nrow=1, ncol=2, more=T)),
  main="Year", xlab="")
```

```{r}
fool_replacement_effect_year_AmE <- effect(
  "year_c",  m_long_fool_replacement, confidence.level=.95,
  xlevels=list(
    year_c=seq(min(subset(data_long_fool_replacement, variety=="AmE")$year_c), 
               max(subset(data_long_fool_replacement, variety=="AmE")$year_c), 
               length.out=50)))
```

```{r}
data_long_fool_replacement_AmE <- subset(
  data_long_fool_replacement, variety=="AmE")
```


```{r fig.height=3.3, fig.width=3.3}
x_breaks_AmE = seq(min(data_long_fool_replacement_AmE$year_c), 
               max(data_long_fool_replacement_AmE$year_c), length.out=5)

plot1 <- xyplot(
  1~1, type="n", xlim=c(-6,.5), ylim=c(0,1),
  ylab="Verbal interpretators (%)", xlab="",
  par.settings=my_settings, axis=axis_all,
  scales=list(x=list(at=c(-6,-4,-2, 0), label=c(1700, 1800, 1900, 2000)),
              y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
  panel=function(x,y){
    panel.polygon(y=plogis(c(fool_replacement_effect_year_AmE$lower, rev(fool_replacement_effect_year_AmE$upper))),
                  x=c(fool_replacement_effect_year_AmE$x$year_c, rev(fool_replacement_effect_year_AmE$x$year_c)),
                  border=F, col="steelblue3", alpha=.3)

    panel.points(y=plogis(fool_replacement_effect_year_AmE$fit), x=fool_replacement_effect_year_AmE$x$year_c, type="l", col="steelblue3")

    panel.dotdiagram(subset(data_long_fool_replacement_AmE, interpretator_verbal==1)$year_c, 
                     y_anchor = 1.22, 
                     seq_min=-6, seq_max=.5, n_bins = 90, scale_y = .015, downwards = F,
                     set_cex=.3, set_pch=19, set_col = "steelblue3")
    
    panel.dotdiagram(subset(data_long_fool_replacement_AmE, interpretator_verbal==0)$year_c, 
                     y_anchor = 1.22, 
                     seq_min=-6, seq_max=.5, n_bins = 90, scale_y = .015, downwards = T,
                     set_cex=.3, set_pch=1, set_col = "steelblue3")

    panel.points(y=tapply(data_long_fool_replacement_AmE$interpretator_verbal, 
                          cut(data_long_fool_replacement_AmE$year_c, 
                              breaks = x_breaks_AmE), mean),
                 x=(x_breaks_AmE[1:4] + x_breaks_AmE[2:5])/2, col="steelblue3", type="l",
                 lty=3, alpha=.5, lwd=1, lineend="square")
    
    panel.points(y=tapply(data_long_fool_replacement_AmE$interpretator_verbal, 
                          cut(data_long_fool_replacement_AmE$year_c, 
                              breaks = x_breaks_AmE), mean),
                 x=(x_breaks_AmE[1:4] + x_breaks_AmE[2:5])/2, pch=21, col="steelblue3", 
                 cex=.3, alpha=.5)
    
    
    panel.text(x=.8, y=c(1.22), label=c("AmE"), adj=0, cex=.8,
               col=c("steelblue3"))
    
    panel.segments(x0=-6, x1=.5, y0=c(1.22), y1=c(1.22), lwd=.5, col="grey40")
    panel.text(x=-6, y=c(1.18, 1.26), label=c("nominal", "verbal"), adj=0, cex=.6, col="grey40")
    panel.text(x=-5.8, y=.93, label="fool", font=3, adj=0)
    })


print(plot1, position=c(0,0,.89,.7))

cairo_pdf("./figures/fool_replacement.pdf", width=3.3, height=3.3)
print(plot1, position=c(0,0,.89,.7))
dev.off()
```




# Combined display

```{r fig.height=3, fig.width=6}
plot1 <- xyplot(1~1, type="n", xlim=c(-5,.5), ylim=c(0,1),
       ylab="Verbal interpretators (%)", xlab="", xlab.top="Verb\n",
       par.settings=my_settings, axis=axis_L,
       scales=list(x=list(at=c(-4,-2, 0), label=c(1800, 1900, 2000)),
                   y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
       panel=function(x,y){
         panel.polygon(y=plogis(c(deceive_replacement_effect_year_AmE$lower, 
                                  rev(deceive_replacement_effect_year_AmE$upper))),
                       x=c(deceive_replacement_effect_year_AmE$x$year_c, 
                           rev(deceive_replacement_effect_year_AmE$x$year_c)),
                       border=F, col="grey", alpha=.3)
         panel.polygon(y=plogis(c(delude_replacement_effect_year_AmE$lower, 
                                  rev(delude_replacement_effect_year_AmE$upper))),
                       x=c(delude_replacement_effect_year_AmE$x$year_c, 
                           rev(delude_replacement_effect_year_AmE$x$year_c)),
                       border=F, col="grey", alpha=.3)
         panel.polygon(y=plogis(c(fool_replacement_effect_year_AmE$lower, 
                                  rev(fool_replacement_effect_year_AmE$upper))),
                       x=c(fool_replacement_effect_year_AmE$x$year_c, 
                           rev(fool_replacement_effect_year_AmE$x$year_c)),
                       border=F, col="grey", alpha=.3)
         
         panel.points(y=plogis(deceive_replacement_effect_year_AmE$fit), 
                      x=deceive_replacement_effect_year_AmE$x$year_c, type="l", col=1)
         panel.points(y=plogis(delude_replacement_effect_year_AmE$fit), 
                      x=delude_replacement_effect_year_AmE$x$year_c, type="l", col=1)
         panel.points(y=plogis(fool_replacement_effect_year_AmE$fit),
                      x=fool_replacement_effect_year_AmE$x$year_c, type="l", col=1)
         
         panel.text(x=c(-2.5, -4.2, -.7), y=c(.8, .3, .5), label=c("fool", "deceive", "delude"), font=3, cex=.9)
         panel.text(x=-5, y=-.2, label="Variety: AmE; Genre: Fiction", adj=0, cex=.7, col="grey30")
       })

plot2 <- xyplot(1~1, type="n", xlim=c(.8, 2.2), ylim=c(0,1),
       ylab="", xlab="", xlab.top="Variety\n",
       par.settings=my_settings, axis=axis_L,
       scales=list(x=list(at=c(1,2), label=c("AmE", "BrE")),
                   y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
       panel=function(x,y){
         panel.points(x=1:2, y=plogis(delude_replacement_effect_variety$fit),
                      type="l", col=1)
         panel.points(x=1:2, y=plogis(delude_replacement_effect_variety$fit),
                      type="p", col=1, pch=21, fill="white", cex=.6)
         
         panel.points(x=1:2, y=plogis(deceive_replacement_effect_variety$fit), 
                      type="l", col=1)
         panel.points(x=1:2, y=plogis(deceive_replacement_effect_variety$fit), 
                      type="p", col=1, pch=19, cex=.6)
         
         panel.text(x=2.1, y=plogis(c(delude_replacement_effect_variety$fit[2],
                                      deceive_replacement_effect_variety$fit[2]))+c(.01,.05),
                    label=c("delude", "deceive"), font=3, cex=.8, adj=0)
         panel.text(x=.8, y=-.2, label="Comparison at the cross-varietal", 
                    adj=0, cex=.7, col="grey30")
         panel.text(x=.8, y=-.25, label="average of 50% verbal interpretators",
                    adj=0, cex=.7, col="grey30")
       })

print(plot1, position=c(0,.05,.55,1), more=T)
print(plot2, position=c(.58,.05,.86,1))

cairo_pdf("./figures/summary_replacement.pdf", width=5, height=2.75)
print(plot1, position=c(0,.05,.55,1), more=T)
print(plot2, position=c(.58,.05,.86,1))
dev.off()
```

