---
title: "Mid-term diachronic perspective: Loss of interpretators in AmE"
output: html_document
---


```{r}
library(tidyverse)
library(effects)
library(lattice)
library(latticeExtra)
library(vcd)
library(car)
library(arm)

source("./r_utils/my_utils.R")

all_data <- read.csv("./data/all_data.csv", stringsAsFactors = T)
all_data$transitivity <- factor(all_data$transitivity, levels=c("transitive", "reflexive", "passive"))
contrasts(all_data$variety) <- contr.sum(2)
contrasts(all_data$transitivity) <- contr.sum(3)
contrasts(all_data$negation) <- contr.sum(2)

all_data$genre_binary <- factor(ifelse(all_data$macro_genre=="fiction", "fiction", "non"))
all_data$genre_binary <- factor(all_data$genre_binary, levels=c("non", "fiction"))

contrasts(all_data$genre_binary) <- contr.sum(2)
data_mid <- subset(all_data, variety=="AmE" & year >= 1810)
```


# Deceive

## Data
```{r}
data_mid_deceive <- subset(data_mid, verb == "deceive")
rownames(data_mid_deceive) <- 1:nrow(data_mid_deceive)
```

## Data inspection
```{r}
structable(genre_binary ~ year_bins_40, data_mid_deceive)
```

```{r fig.height=3, fig.width=4.5}
data_mid_deceive %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=2) +  
  facet_grid(rows=vars(genre_binary)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") + xlim(1810, 2020) +
  labs(title="Deceive",
       subtitle="Cases by Year and Genre (AmE)")
```

```{r fig.height=4, fig.width=4.5}
data_mid_deceive %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=2) +
  facet_grid(rows=vars(transitivity)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") + xlim(1810, 2020) +
  labs(title="Deceive",
       subtitle="Cases by Year and Transitivity (AmE)")
```

```{r fig.height=3, fig.width=4.5}
data_mid_deceive %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=2) +  
  facet_grid(rows=vars(negation)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") + xlim(1810, 2020) +
  labs(title="Deceive",
       subtitle="Cases by Year and Negation (AmE)")
```


## Model 
```{r}
m_mid_deceive <- glm(
  interpretator_present ~ year_c + genre_binary + transitivity + negation, 
  data=data_mid_deceive, family="binomial")

display(m_mid_deceive)
```

## Model checking

Residual plots
```{r fig.height=2.5, fig.width=10}
residualPlots(m_mid_deceive, layout=c(1,5), tests = F, ask=F)
```

Marginal model plots
```{r fig.height=3, fig.width=5, warning=F}
marginalModelPlots(m_mid_deceive, layout=c(1,2))
```

Influence diagnostics
```{r fig.height=4, fig.width=4}
outlier_id <- influencePlot(m_mid_deceive)
```

Effect of influential cases on coefficients + SEs
```{r}
outlier_id <- as.integer(rownames(outlier_id))

m_mid_deceive_1 <- update(m_mid_deceive, subset=-outlier_id[1])
m_mid_deceive_2 <- update(m_mid_deceive, subset=-outlier_id[2])
m_mid_deceive_3 <- update(m_mid_deceive, subset=-outlier_id[3])
m_mid_deceive_4 <- update(m_mid_deceive, subset=-outlier_id[4])
m_mid_deceive_5 <- update(m_mid_deceive, subset=-outlier_id[5])
m_mid_deceive_all <- update(m_mid_deceive, subset=-outlier_id)

coef_change <-compareCoefs(
  m_mid_deceive, 
  m_mid_deceive_1,
  m_mid_deceive_2, 
  m_mid_deceive_3,
  m_mid_deceive_4,
  m_mid_deceive_5,
  m_mid_deceive_all, digits=2)
```

```{r fig.height=2, fig.width=8}
plot1 <- xyplot(as.numeric(coef_change[4,]) ~ 1:length(coef_change[4,]),
       scales=list(x=list(at=1:7,labels=1:7)),
       par.settings=my_settings, axis=axis_L, ylim=c(-2.1,.1), pch=19,
       xlab.top="Year (95% CI)",
       xlab="", ylab="",
       panel=function(x,y,...){
         panel.xyplot(x,y,...)
         panel.abline(h=0, col="grey")
         panel.arrows(x0=x, x1=x, 
                      y0=y-2*as.numeric(coef_change[5,]), 
                      y1=y+2*as.numeric(coef_change[5,]),
                      code=3, angle=90, length=.03)
       })
plot2 <- xyplot(as.numeric(coef_change[7,]) ~ 1:length(coef_change[7,]),
       scales=list(x=list(at=1:7,labels=1:7)),
       par.settings=my_settings, axis=axis_L, ylim=c(-.2,1.2), pch=19,
       xlab.top="Genre (95% CI)",
       xlab="", ylab="",
       panel=function(x,y,...){
         panel.xyplot(x,y,...)
         panel.abline(h=0, col="grey")
         panel.arrows(x0=x, x1=x, 
                      y0=y-2*as.numeric(coef_change[8,]), 
                      y1=y+2*as.numeric(coef_change[8,]),
                      code=3, angle=90, length=.03)
       })
plot3 <- xyplot(as.numeric(coef_change[16,]) ~ 1:length(coef_change[16,]),
       scales=list(x=list(at=1:7,labels=1:7)),
       par.settings=my_settings, axis=axis_L, ylim=c(-.2,1.2), pch=19,
       xlab.top="Negation (95% CI)",
       xlab="", ylab="",
       panel=function(x,y,...){
         panel.xyplot(x,y,...)
         panel.abline(h=0, col="grey")
         panel.arrows(x0=x, x1=x, 
                      y0=y-2*as.numeric(coef_change[17,]), 
                      y1=y+2*as.numeric(coef_change[17,]),
                      code=3, angle=90, length=.03)
       })
plot4 <- xyplot(as.numeric(coef_change[10,]) ~ 1:length(coef_change[10,]),
       scales=list(x=list(at=1:7,labels=1:7)),
       par.settings=my_settings, axis=axis_L, ylim=c(-2,2), pch=19,
       xlab.top="Transitivity (95% CI)",
       xlab="", ylab="",
       panel=function(x,y,...){
         panel.xyplot(x,y,...)
         panel.points(x=c(1:7)+.1,y=as.numeric(coef_change[13,]),pch=19,col=1)
         panel.abline(h=0, col="grey")
         panel.arrows(x0=x, x1=x, 
                      y0=y-2*as.numeric(coef_change[11,]), 
                      y1=y+2*as.numeric(coef_change[11,]),
                      code=3, angle=90, length=.03)
         panel.arrows(x0=x+.1, x1=x+.1, 
                      y0=as.numeric(coef_change[13,])-2*as.numeric(coef_change[14,]), 
                      y1=as.numeric(coef_change[13,])+2*as.numeric(coef_change[14,]),
                      code=3, angle=90, length=.03)
       })
cowplot::plot_grid(plot1, plot2, plot3, plot4, ncol=4)
```
```{r}
data_mid_deceive[outlier_id,]
```

## Model visualization

```{r fig.width=10, fig.height=3}
plot(effects::predictorEffect(
  "year_c",
  m_mid_deceive, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    genre_binary1 = 0,
    transitivity1 = 0,
    transitivity2 = 0,
    negation1 = 0))), 
  axes=list(y=list(type="response", lim=c(0,1))),
  lattice=list(array=list(row=1, col=1, nrow=1, ncol=4, more=T)),
  main="Year", xlab="")

plot(effects::predictorEffect(
  "genre_binary",
  m_mid_deceive, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    year_c = 0,
    transitivity1 = 0,
    transitivity2 = 0,
    negation1 = 0))), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=2, nrow=1, ncol=4, more=T)),
  main="Genre", xlab="", ylab="")

plot(effects::predictorEffect(
  "negation",
  m_mid_deceive, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    genre_binary1 = 0,
    transitivity1 = 0,
    transitivity2 = 0,
    year_c = 0))), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=3, nrow=1, ncol=4, more=T)),
  main="Negation", xlab="", ylab="")

plot(effects::predictorEffect(
  "transitivity",
  m_mid_deceive, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    genre_binary1 = 0,
    year_c = 0,
    negation1 = 0))), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=4, nrow=1, ncol=4, more=T)),
  main="Transitivity", xlab="", ylab="")
```
```{r}
str(data_mid_deceive)
```


```{r}
arm::display(m_mid_deceive)

deceive_effect_year <- effect(
  "year_c",  m_mid_deceive, confidence.level=.95,
  xlevels=list(
    year_c=seq(min(data_mid_deceive$year_c), 
               max(data_mid_deceive$year_c), 
               length.out=50)),
  fixed.predictors=list(given.values=c(
    genre_binary1 = 0,
    transitivity1 = 0,
    transitivity2  = 0,
    negation1 = 0)))

deceive_effect_genre <- effect(
  "genre_binary",  m_mid_deceive, confidence.level=.95,
  fixed.predictors=list(given.values=c(
    year_c = 0,
    transitivity1 = 0,
    transitivity2  = 0,
    negation1 = 0)))

deceive_effect_negation <- effect(
  "negation",  m_mid_deceive, confidence.level=.95,
  fixed.predictors=list(given.values=c(
    genre_binary1 = 0,
    transitivity1 = 0,
    transitivity2  = 0,
    year_c = 0)))

deceive_effect_transitivity <- effect(
  "transitivity",  m_mid_deceive, confidence.level=.95,
  fixed.predictors=list(given.values=c(
    genre_binary1 = 0,
    year_c = 0,
    negation1 = 0)))

```


```{r fig.height=2.5, fig.width=7}
x_breaks = seq(min(data_mid_deceive$year_c), 
               max(data_mid_deceive$year_c), length.out=6)

plot1 <- xyplot(
  1~1, type="n", xlim=c(-4,.5), ylim=c(0,1),
  ylab="Interpretator present (%)", xlab="", xlab.top="Year\n",
  par.settings=my_settings, axis=axis_L,
  scales=list(x=list(at=c(-4,-2, 0), label=c(1800, 1900, 2000)),
              y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
  panel=function(x,y){
    panel.polygon(y=plogis(c(deceive_effect_year$lower, rev(deceive_effect_year$upper))),
                  x=c(deceive_effect_year$x$year_c, rev(deceive_effect_year$x$year_c)),
                  border=F, col="grey", alpha=.5)
    panel.points(y=plogis(deceive_effect_year$fit), 
                 x=deceive_effect_year$x$year_c, type="l", col=1)
    panel.text(x=-4, y=-.2, label="Estimates adjusted to: Year = 2000; Genre, Negation, Transitivity: Simple average over conditions", adj=0, cex=.7, col="grey30")
    })

plot2 <- xyplot(
  1~1, type="n", xlim=c(.8, 2.2), ylim=c(0,1),
  ylab=" ", xlab="", xlab.top="Genre\n",
  par.settings=my_settings, axis=axis_L,
  scales=list(x=list(at=c(1,2), label=c("Non", "Fiction")),
              y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
  panel=function(x,y){
    panel.points(y=plogis(deceive_effect_genre$fit), x=1:2, type="l", col=1)
    panel.points(y=plogis(deceive_effect_genre$fit), x=1:2, 
                 type="p", col=1, pch=19, cex=.6)
    
    panel.segments(x0=1:2, x1=1:2, y0=plogis(deceive_effect_genre$upper), 
                   y1=plogis(deceive_effect_genre$lower))
    })


plot3 <- xyplot(
  1~1, type="n", xlim=c(.8, 2.2), ylim=c(0,1),
  ylab=" ", xlab="", xlab.top="Negation\n",
  par.settings=my_settings, axis=axis_L,
  scales=list(x=list(at=c(1,2), label=c("No", "Yes")),
              y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
  panel=function(x,y){
    panel.points(y=plogis(deceive_effect_negation$fit), x=1:2, type="l", col=1)
    panel.points(y=plogis(deceive_effect_negation$fit), x=1:2, 
                 type="p", col=1, pch=19, cex=.6)
    
    panel.segments(x0=1:2, x1=1:2, y0=plogis(deceive_effect_negation$upper), 
                   y1=plogis(deceive_effect_negation$lower))
    })


plot4 <- xyplot(
  1~1, type="n", xlim=c(.8, 3.2), ylim=c(0,1),
  ylab=" ", xlab="", xlab.top="Transitivity\n",
  par.settings=my_settings, axis=axis_L,
  scales=list(x=list(at=c(1,2,3), label=c("Tran", "Refl", "Pass")),
              y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
  panel=function(x,y){
    panel.points(y=plogis(deceive_effect_transitivity$fit), x=1:3, type="l", col=1)
    panel.points(y=plogis(deceive_effect_transitivity$fit), x=1:3, 
                 type="p", col=1, pch=19, cex=.6)
    
    panel.segments(x0=1:3, x1=1:3, y0=plogis(deceive_effect_transitivity$upper), 
                   y1=plogis(deceive_effect_transitivity$lower))
    })


print(plot1, position=c(0,0,.35,1), more=T)
print(plot2, position=c(.35,0,.55,1), more=T)
print(plot3, position=c(.55,0,.75,1), more=T)
print(plot4, position=c(.75,0,1,1))


cairo_pdf("./figures/deceive_midterm_perspective.pdf", width=7, height=2.5)
print(plot1, position=c(0,0,.35,1), more=T)
print(plot2, position=c(.35,0,.55,1), more=T)
print(plot3, position=c(.55,0,.75,1), more=T)
print(plot4, position=c(.75,0,1,1))
dev.off()
```







# Delude

## Data
```{r}
data_mid_delude <- subset(data_mid, verb == "delude")
rownames(data_mid_delude) <- 1:nrow(data_mid_delude)
```

## Data inspection
```{r}
structable(genre_binary ~ year_bins_40, data_mid_delude)
```

```{r fig.height=3, fig.width=4.5}
data_mid_delude %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=2) +  
  facet_grid(rows=vars(genre_binary)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") + xlim(1810, 2020) +
  labs(title="Delude",
       subtitle="Cases by Year and Genre (AmE)")
```

```{r fig.height=4, fig.width=4.5}
data_mid_delude %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=2) +
  facet_grid(rows=vars(transitivity)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") + xlim(1810, 2020) +
  labs(title="Delude",
       subtitle="Cases by Year and Transitivity (AmE)")
```

```{r fig.height=3, fig.width=4.5}
data_mid_delude %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=2) +  
  facet_grid(rows=vars(negation)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") + xlim(1810, 2020) +
  labs(title="Delude",
       subtitle="Cases by Year and Negation (AmE)")
```


## Model 
```{r}
m_mid_delude <- glm(
  interpretator_present ~ year_c + genre_binary + transitivity + negation, 
  data=data_mid_delude, family="binomial")

display(m_mid_delude)
```

## Model checking

Residual plots
```{r fig.height=2.5, fig.width=10}
residualPlots(m_mid_delude, layout=c(1,5), tests = F, ask=F)
```

Marginal model plots
```{r fig.height=3, fig.width=5, warning=F}
marginalModelPlots(m_mid_delude, layout=c(1,2))
```

Influence diagnostics
```{r fig.height=4, fig.width=4}
outlier_id <- influencePlot(m_mid_delude)
```

Effect of influential cases on coefficients + SEs
```{r}
outlier_id <- as.integer(rownames(outlier_id))

m_mid_delude_1 <- update(m_mid_delude, subset=-outlier_id[1])
m_mid_delude_2 <- update(m_mid_delude, subset=-outlier_id[2])
m_mid_delude_3 <- update(m_mid_delude, subset=-outlier_id[3])
m_mid_delude_4 <- update(m_mid_delude, subset=-outlier_id[4])
m_mid_delude_5 <- update(m_mid_delude, subset=-outlier_id[5])
m_mid_delude_all <- update(m_mid_delude, subset=-outlier_id)

coef_change <- compareCoefs(
  m_mid_delude, 
  m_mid_delude_1,
  m_mid_delude_2, 
  m_mid_delude_3,
  m_mid_delude_4,
  m_mid_delude_5,
  m_mid_delude_all, digits=2)
```
```{r fig.height=2, fig.width=8}
plot1 <- xyplot(as.numeric(coef_change[4,]) ~ 1:length(coef_change[4,]),
       scales=list(x=list(at=1:7,labels=1:7)),
       par.settings=my_settings, axis=axis_L, ylim=c(-2.1,.1), pch=19,
       xlab.top="Year (95% CI)",
       xlab="", ylab="",
       panel=function(x,y,...){
         panel.xyplot(x,y,...)
         panel.abline(h=0, col="grey")
         panel.arrows(x0=x, x1=x, 
                      y0=y-2*as.numeric(coef_change[5,]), 
                      y1=y+2*as.numeric(coef_change[5,]),
                      code=3, angle=90, length=.03)
       })
plot2 <- xyplot(as.numeric(coef_change[7,]) ~ 1:length(coef_change[7,]),
       scales=list(x=list(at=1:7,labels=1:7)),
       par.settings=my_settings, axis=axis_L, ylim=c(-.2,1.2), pch=19,
       xlab.top="Genre (95% CI)",
       xlab="", ylab="",
       panel=function(x,y,...){
         panel.xyplot(x,y,...)
         panel.abline(h=0, col="grey")
         panel.arrows(x0=x, x1=x, 
                      y0=y-2*as.numeric(coef_change[8,]), 
                      y1=y+2*as.numeric(coef_change[8,]),
                      code=3, angle=90, length=.03)
       })
plot3 <- xyplot(as.numeric(coef_change[16,]) ~ 1:length(coef_change[16,]),
       scales=list(x=list(at=1:7,labels=1:7)),
       par.settings=my_settings, axis=axis_L, ylim=c(-.2,1.2), pch=19,
       xlab.top="Negation (95% CI)",
       xlab="", ylab="",
       panel=function(x,y,...){
         panel.xyplot(x,y,...)
         panel.abline(h=0, col="grey")
         panel.arrows(x0=x, x1=x, 
                      y0=y-2*as.numeric(coef_change[17,]), 
                      y1=y+2*as.numeric(coef_change[17,]),
                      code=3, angle=90, length=.03)
       })
plot4 <- xyplot(as.numeric(coef_change[10,]) ~ 1:length(coef_change[10,]),
       scales=list(x=list(at=1:7,labels=1:7)),
       par.settings=my_settings, axis=axis_L, ylim=c(-3.5,4), pch=19,
       xlab.top="Transitivity (95% CI)",
       xlab="", ylab="",
       panel=function(x,y,...){
         panel.xyplot(x,y,...)
         panel.points(x=c(1:7)+.1,y=as.numeric(coef_change[13,]),pch=19,col=1)
         panel.abline(h=0, col="grey")
         panel.arrows(x0=x, x1=x, 
                      y0=y-2*as.numeric(coef_change[11,]), 
                      y1=y+2*as.numeric(coef_change[11,]),
                      code=3, angle=90, length=.03)
         panel.arrows(x0=x+.1, x1=x+.1, 
                      y0=as.numeric(coef_change[13,])-2*as.numeric(coef_change[14,]), 
                      y1=as.numeric(coef_change[13,])+2*as.numeric(coef_change[14,]),
                      code=3, angle=90, length=.03)
       })
cowplot::plot_grid(plot1, plot2, plot3, plot4, ncol=4)
```

```{r}
data_mid_delude[outlier_id,]
```

## Model visualization

```{r fig.width=10, fig.height=3}
plot(effects::predictorEffect(
  "year_c",
  m_mid_delude, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    genre_binary1 = 0,
    transitivity1 = 0,
    transitivity2 = 0,
    negation1 = 0))), 
  axes=list(y=list(type="response", lim=c(0,1))),
  lattice=list(array=list(row=1, col=1, nrow=1, ncol=4, more=T)),
  main="Year", xlab="")

plot(effects::predictorEffect(
  "genre_binary",
  m_mid_delude, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    year_c = 0,
    transitivity1 = 0,
    transitivity2 = 0,
    negation1 = 0))), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=2, nrow=1, ncol=4, more=T)),
  main="Genre", xlab="", ylab="")

plot(effects::predictorEffect(
  "negation",
  m_mid_delude, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    genre_binary1 = 0,
    transitivity1 = 0,
    transitivity2 = 0,
    year_c = 0))), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=3, nrow=1, ncol=4, more=T)),
  main="Negation", xlab="", ylab="")

plot(effects::predictorEffect(
  "transitivity",
  m_mid_delude, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    genre_binary1 = 0,
    year_c = 0,
    negation1 = 0))), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=4, nrow=1, ncol=4, more=T)),
  main="Transitivity", xlab="", ylab="")
```


```{r}
delude_effect_year <- effect(
  "year_c",  m_mid_delude, confidence.level=.95,
  xlevels=list(
    year_c=seq(min(data_mid_delude$year_c), 
               max(data_mid_delude$year_c), 
               length.out=50)),
  fixed.predictors=list(given.values=c(
    genre_binary1 = 0,
    transitivity1 = 0,
    transitivity2  = 0,
    negation1 = 0)))

delude_effect_genre <- effect(
  "genre_binary",  m_mid_delude, confidence.level=.95,
  fixed.predictors=list(given.values=c(
    year_c = 0,
    transitivity1 = 0,
    transitivity2  = 0,
    negation1 = 0)))

delude_effect_negation <- effect(
  "negation",  m_mid_delude, confidence.level=.95,
  fixed.predictors=list(given.values=c(
    genre_binary1 = 0,
    transitivity1 = 0,
    transitivity2  = 0,
    year_c = 0)))

delude_effect_transitivity <- effect(
  "transitivity",  m_mid_delude, confidence.level=.95,
  fixed.predictors=list(given.values=c(
    genre_binary1 = 0,
    year_c = 0,
    negation1 = 0)))

```



```{r fig.height=2.5, fig.width=7}
x_breaks = seq(min(data_mid_delude$year_c), 
               max(data_mid_delude$year_c), length.out=6)

plot1 <- xyplot(
  1~1, type="n", xlim=c(-4,.5), ylim=c(0,1),
  ylab="Interpretator present (%)", xlab="", xlab.top="Year\n",
  par.settings=my_settings, axis=axis_L,
  scales=list(x=list(at=c(-4,-2, 0), label=c(1800, 1900, 2000)),
              y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
  panel=function(x,y){
    panel.polygon(y=plogis(c(delude_effect_year$lower, rev(delude_effect_year$upper))),
                  x=c(delude_effect_year$x$year_c, rev(delude_effect_year$x$year_c)),
                  border=F, col="grey", alpha=.5)
    panel.points(y=plogis(delude_effect_year$fit), 
                 x=delude_effect_year$x$year_c, type="l", col=1)
    panel.text(x=-4, y=-.2, label="Estimates adjusted to: Year = 2000; Genre, Negation, Transitivity: Simple average over conditions", adj=0, cex=.7, col="grey30")
    })

plot2 <- xyplot(
  1~1, type="n", xlim=c(.8, 2.2), ylim=c(0,1),
  ylab=" ", xlab="", xlab.top="Genre\n",
  par.settings=my_settings, axis=axis_L,
  scales=list(x=list(at=c(1,2), label=c("Non", "Fiction")),
              y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
  panel=function(x,y){
    panel.points(y=plogis(delude_effect_genre$fit), x=1:2, type="l", col=1)
    panel.points(y=plogis(delude_effect_genre$fit), x=1:2, 
                 type="p", col=1, pch=19, cex=.6)
    
    panel.segments(x0=1:2, x1=1:2, y0=plogis(delude_effect_genre$upper), 
                   y1=plogis(delude_effect_genre$lower))
    })


plot3 <- xyplot(
  1~1, type="n", xlim=c(.8, 2.2), ylim=c(0,1),
  ylab=" ", xlab="", xlab.top="Negation\n",
  par.settings=my_settings, axis=axis_L,
  scales=list(x=list(at=c(1,2), label=c("No", "Yes")),
              y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
  panel=function(x,y){
    panel.points(y=plogis(delude_effect_negation$fit), x=1:2, type="l", col=1)
    panel.points(y=plogis(delude_effect_negation$fit), x=1:2, 
                 type="p", col=1, pch=19, cex=.6)
    
    panel.segments(x0=1:2, x1=1:2, y0=plogis(delude_effect_negation$upper), 
                   y1=plogis(delude_effect_negation$lower))
    })


plot4 <- xyplot(
  1~1, type="n", xlim=c(.8, 3.2), ylim=c(0,1),
  ylab=" ", xlab="", xlab.top="Transitivity\n",
  par.settings=my_settings, axis=axis_L,
  scales=list(x=list(at=c(1,2,3), label=c("Tran", "Refl", "Pass")),
              y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
  panel=function(x,y){
    panel.points(y=plogis(delude_effect_transitivity$fit), x=1:3, type="l", col=1)
    panel.points(y=plogis(delude_effect_transitivity$fit), x=1:3, 
                 type="p", col=1, pch=19, cex=.6)
    
    panel.segments(x0=1:3, x1=1:3, y0=plogis(delude_effect_transitivity$upper), 
                   y1=plogis(delude_effect_transitivity$lower))
    })


print(plot1, position=c(0,0,.35,1), more=T)
print(plot2, position=c(.35,0,.55,1), more=T)
print(plot3, position=c(.55,0,.75,1), more=T)
print(plot4, position=c(.75,0,1,1))


cairo_pdf("./figures/delude_midterm_perspective.pdf", width=7, height=2.5)
print(plot1, position=c(0,0,.35,1), more=T)
print(plot2, position=c(.35,0,.55,1), more=T)
print(plot3, position=c(.55,0,.75,1), more=T)
print(plot4, position=c(.75,0,1,1))
dev.off()
```









# Fool

## Data
```{r}
data_mid_fool <- subset(data_mid, verb == "fool")
rownames(data_mid_fool) <- 1:nrow(data_mid_fool)
```

## Data inspection
```{r}
structable(genre_binary ~ year_bins_40, data_mid_fool)
```

```{r fig.height=3, fig.width=4.5}
data_mid_fool %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=2) +  
  facet_grid(rows=vars(genre_binary)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") + xlim(1810, 2020) +
  labs(title="Fool",
       subtitle="Cases by Year and Genre (AmE)")
```

```{r fig.height=4, fig.width=4.5}
data_mid_fool %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=2) +
  facet_grid(rows=vars(transitivity)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") + xlim(1810, 2020) +
  labs(title="Fool",
       subtitle="Cases by Year and Transitivity (AmE)")
```

```{r fig.height=3, fig.width=4.5}
data_mid_fool %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=2) +  
  facet_grid(rows=vars(negation)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") + xlim(1810, 2020) +
  labs(title="Fool",
       subtitle="Cases by Year and Negation (AmE)")
```


## Model 
```{r}
m_mid_fool <- glm(
  interpretator_present ~ year_c + genre_binary + transitivity + negation, 
  data=data_mid_fool, family="binomial")

display(m_mid_fool)
```

## Model checking

Residual plots
```{r fig.height=2.5, fig.width=10}
residualPlots(m_mid_fool, layout=c(1,5), tests = F, ask=F)
```

Marginal model plots
```{r fig.height=3, fig.width=5, warning=F}
marginalModelPlots(m_mid_fool, layout=c(1,2))
```

Influence diagnostics
```{r fig.height=4, fig.width=4}
outlier_id <- influencePlot(m_mid_fool)
```

Effect of influential cases on coefficients + SEs
```{r}
outlier_id <- as.integer(rownames(outlier_id))

m_mid_fool_1 <- update(m_mid_fool, subset=-outlier_id[1])
m_mid_fool_2 <- update(m_mid_fool, subset=-outlier_id[2])
m_mid_fool_3 <- update(m_mid_fool, subset=-outlier_id[3])
m_mid_fool_4 <- update(m_mid_fool, subset=-outlier_id[4])
m_mid_fool_5 <- update(m_mid_fool, subset=-outlier_id[5])
m_mid_fool_6 <- update(m_mid_fool, subset=-outlier_id[6])
m_mid_fool_all <- update(m_mid_fool, subset=-outlier_id)

coef_change <- compareCoefs(
  m_mid_fool, 
  m_mid_fool_1,
  m_mid_fool_2, 
  m_mid_fool_3,
  m_mid_fool_4,
  m_mid_fool_5,
  m_mid_fool_6, 
  m_mid_fool_all, digits=2)
```
```{r fig.height=2, fig.width=8}
plot1 <- xyplot(as.numeric(coef_change[4,]) ~ 1:length(coef_change[4,]),
       scales=list(x=list(at=1:8,labels=1:8)),
       par.settings=my_settings, axis=axis_L, ylim=c(-1,2), pch=19,
       xlab.top="Year (95% CI)",
       xlab="", ylab="",
       panel=function(x,y,...){
         panel.xyplot(x,y,...)
         panel.abline(h=0, col="grey")
         panel.arrows(x0=x, x1=x, 
                      y0=y-2*as.numeric(coef_change[5,]), 
                      y1=y+2*as.numeric(coef_change[5,]),
                      code=3, angle=90, length=.03)
       })
plot2 <- xyplot(as.numeric(coef_change[7,]) ~ 1:length(coef_change[7,]),
       scales=list(x=list(at=1:8,labels=1:8)),
       par.settings=my_settings, axis=axis_L, ylim=c(-1,.8), pch=19,
       xlab.top="Genre (95% CI)",
       xlab="", ylab="",
       panel=function(x,y,...){
         panel.xyplot(x,y,...)
         panel.abline(h=0, col="grey")
         panel.arrows(x0=x, x1=x, 
                      y0=y-2*as.numeric(coef_change[8,]), 
                      y1=y+2*as.numeric(coef_change[8,]),
                      code=3, angle=90, length=.03)
       })
plot3 <- xyplot(as.numeric(coef_change[16,]) ~ 1:length(coef_change[16,]),
       scales=list(x=list(at=1:7,labels=1:7)),
       par.settings=my_settings, axis=axis_L, ylim=c(-.2,1.2), pch=19,
       xlab.top="Negation (95% CI)",
       xlab="", ylab="",
       panel=function(x,y,...){
         panel.xyplot(x,y,...)
         panel.abline(h=0, col="grey")
         panel.arrows(x0=x, x1=x, 
                      y0=y-2*as.numeric(coef_change[17,]), 
                      y1=y+2*as.numeric(coef_change[17,]),
                      code=3, angle=90, length=.03)
       })
plot4 <- xyplot(as.numeric(coef_change[10,]) ~ 1:length(coef_change[10,]),
       scales=list(x=list(at=1:8,labels=1:8)),
       par.settings=my_settings, axis=axis_L, ylim=c(-3,3), pch=19,
       xlab.top="Transitivity (95% CI)",
       xlab="", ylab="",
       panel=function(x,y,...){
         panel.xyplot(x,y,...)
         panel.points(x=c(1:8)+.1,y=as.numeric(coef_change[13,]),pch=19,col=1)
         panel.abline(h=0, col="grey")
         panel.arrows(x0=x, x1=x, 
                      y0=y-2*as.numeric(coef_change[11,]), 
                      y1=y+2*as.numeric(coef_change[11,]),
                      code=3, angle=90, length=.03)
         panel.arrows(x0=x+.1, x1=x+.1, 
                      y0=as.numeric(coef_change[13,])-2*as.numeric(coef_change[14,]), 
                      y1=as.numeric(coef_change[13,])+2*as.numeric(coef_change[14,]),
                      code=3, angle=90, length=.03)
       })
cowplot::plot_grid(plot1, plot2, plot3, plot4, ncol=4)
```

```{r}
data_mid_fool[outlier_id,]
```

## Model visualization

```{r fig.width=10, fig.height=3}
plot(effects::predictorEffect(
  "year_c",
  m_mid_fool, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    genre_binary1 = 0,
    transitivity1 = 0,
    transitivity2 = 0,
    negation1 = 0))), 
  axes=list(y=list(type="response", lim=c(0,1))),
  lattice=list(array=list(row=1, col=1, nrow=1, ncol=4, more=T)),
  main="Year", xlab="")

plot(effects::predictorEffect(
  "genre_binary",
  m_mid_fool, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    year_c = 0,
    transitivity1 = 0,
    transitivity2 = 0,
    negation1 = 0))), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=2, nrow=1, ncol=4, more=T)),
  main="Genre", xlab="", ylab="")

plot(effects::predictorEffect(
  "negation",
  m_mid_fool, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    genre_binary1 = 0,
    transitivity1 = 0,
    transitivity2 = 0,
    year_c = 0))), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=3, nrow=1, ncol=4, more=T)),
  main="Negation", xlab="", ylab="")

plot(effects::predictorEffect(
  "transitivity",
  m_mid_fool, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    genre_binary1 = 0,
    year_c = 0,
    negation1 = 0))), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=4, nrow=1, ncol=4, more=T)),
  main="Transitivity", xlab="", ylab="")
```


```{r}
fool_effect_year <- effect(
  "year_c",  m_mid_fool, confidence.level=.95,
  xlevels=list(
    year_c=seq(min(data_mid_fool$year_c), 
               max(data_mid_fool$year_c), 
               length.out=50)),
  fixed.predictors=list(given.values=c(
    genre_binary1 = 0,
    transitivity1 = 0,
    transitivity2  = 0,
    negation1 = 0)))

fool_effect_genre <- effect(
  "genre_binary",  m_mid_fool, confidence.level=.95,
  fixed.predictors=list(given.values=c(
    year_c = 0,
    transitivity1 = 0,
    transitivity2  = 0,
    negation1 = 0)))

fool_effect_negation <- effect(
  "negation",  m_mid_fool, confidence.level=.95,
  fixed.predictors=list(given.values=c(
    genre_binary1 = 0,
    transitivity1 = 0,
    transitivity2  = 0,
    year_c = 0)))

fool_effect_transitivity <- effect(
  "transitivity",  m_mid_fool, confidence.level=.95,
  fixed.predictors=list(given.values=c(
    genre_binary1 = 0,
    year_c = 0,
    negation1 = 0)))

```


```{r fig.height=2.5, fig.width=7}
x_breaks = seq(min(data_mid_fool$year_c), 
               max(data_mid_fool$year_c), length.out=6)

plot1 <- xyplot(
  1~1, type="n", xlim=c(-4,.5), ylim=c(0,1),
  ylab="Interpretator present (%)", xlab="", xlab.top="Year\n",
  par.settings=my_settings, axis=axis_L,
  scales=list(x=list(at=c(-4,-2, 0), label=c(1800, 1900, 2000)),
              y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
  panel=function(x,y){
    panel.polygon(y=plogis(c(fool_effect_year$lower, rev(fool_effect_year$upper))),
                  x=c(fool_effect_year$x$year_c, rev(fool_effect_year$x$year_c)),
                  border=F, col="grey", alpha=.5)
    panel.points(y=plogis(fool_effect_year$fit), 
                 x=fool_effect_year$x$year_c, type="l", col=1)
    panel.text(x=-4, y=-.2, label="Estimates adjusted to: Year = 2000; Genre, Negation, Transitivity: Simple average over conditions", adj=0, cex=.7, col="grey30")
    })

plot2 <- xyplot(
  1~1, type="n", xlim=c(.8, 2.2), ylim=c(0,1),
  ylab=" ", xlab="", xlab.top="Genre\n",
  par.settings=my_settings, axis=axis_L,
  scales=list(x=list(at=c(1,2), label=c("Fiction", "Non")),
              y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
  panel=function(x,y){
    panel.points(y=plogis(fool_effect_genre$fit), x=1:2, type="l", col=1)
    panel.points(y=plogis(fool_effect_genre$fit), x=1:2, 
                 type="p", col=1, pch=19, cex=.6)
    
    panel.segments(x0=1:2, x1=1:2, y0=plogis(fool_effect_genre$upper), 
                   y1=plogis(fool_effect_genre$lower))
    })


plot3 <- xyplot(
  1~1, type="n", xlim=c(.8, 2.2), ylim=c(0,1),
  ylab=" ", xlab="", xlab.top="Negation\n",
  par.settings=my_settings, axis=axis_L,
  scales=list(x=list(at=c(1,2), label=c("No", "Yes")),
              y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
  panel=function(x,y){
    panel.points(y=plogis(fool_effect_negation$fit), x=1:2, type="l", col=1)
    panel.points(y=plogis(fool_effect_negation$fit), x=1:2, 
                 type="p", col=1, pch=19, cex=.6)
    
    panel.segments(x0=1:2, x1=1:2, y0=plogis(fool_effect_negation$upper), 
                   y1=plogis(fool_effect_negation$lower))
    })


plot4 <- xyplot(
  1~1, type="n", xlim=c(.8, 3.2), ylim=c(0,1),
  ylab=" ", xlab="", xlab.top="Transitivity\n",
  par.settings=my_settings, axis=axis_L,
  scales=list(x=list(at=c(1,2,3), label=c("Tran", "Refl", "Pass")),
              y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
  panel=function(x,y){
    panel.points(y=plogis(fool_effect_transitivity$fit), x=1:3, type="l", col=1)
    panel.points(y=plogis(fool_effect_transitivity$fit), x=1:3, 
                 type="p", col=1, pch=19, cex=.6)
    
    panel.segments(x0=1:3, x1=1:3, y0=plogis(fool_effect_transitivity$upper), 
                   y1=plogis(fool_effect_transitivity$lower))
    })


print(plot1, position=c(0,0,.35,1), more=T)
print(plot2, position=c(.35,0,.55,1), more=T)
print(plot3, position=c(.55,0,.75,1), more=T)
print(plot4, position=c(.75,0,1,1))


cairo_pdf("./figures/fool_midterm_perspective.pdf", width=7, height=2.5)
print(plot1, position=c(0,0,.35,1), more=T)
print(plot2, position=c(.35,0,.55,1), more=T)
print(plot3, position=c(.55,0,.75,1), more=T)
print(plot4, position=c(.75,0,1,1))
dev.off()
```


# Combined display

```{r fig.height=2.5, fig.width=7.5}
x_breaks = seq(min(data_mid_fool$year_c), 
               max(data_mid_fool$year_c), length.out=6)

plot1 <- xyplot(
  1~1, type="n", xlim=c(-4,.5), ylim=c(0,1),
  ylab="Interpretator present (%)", xlab="", xlab.top="Year\n",
  par.settings=my_settings, axis=axis_L,
  scales=list(x=list(at=c(-4,-2, 0), label=c(1800, 1900, 2000)),
              y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
  panel=function(x,y){
    panel.polygon(y=plogis(c(deceive_effect_year$lower, rev(deceive_effect_year$upper))),
                  x=c(deceive_effect_year$x$year_c, rev(deceive_effect_year$x$year_c)),
                  border=F, col="grey", alpha=.5)
    panel.polygon(y=plogis(c(delude_effect_year$lower, rev(delude_effect_year$upper))),
                  x=c(delude_effect_year$x$year_c, rev(delude_effect_year$x$year_c)),
                  border=F, col="grey", alpha=.5)
    panel.polygon(y=plogis(c(fool_effect_year$lower, rev(fool_effect_year$upper))),
                  x=c(fool_effect_year$x$year_c, rev(fool_effect_year$x$year_c)),
                  border=F, col="grey", alpha=.5)
    
    panel.points(y=plogis(deceive_effect_year$fit), 
                 x=deceive_effect_year$x$year_c, type="l", col=1)
    panel.points(y=plogis(delude_effect_year$fit), 
                 x=delude_effect_year$x$year_c, type="l", col=1)
    panel.points(y=plogis(fool_effect_year$fit), 
                 x=fool_effect_year$x$year_c, type="l", col=1)
    panel.text(x=.6, y=c(.95, .7, .6), label=c("fool", "delude", "deceive"),
               font=3, adj=0, cex=.8)
    panel.text(x=-4, y=-.2, label="Estimates adjusted to: Year = 2000; Genre, Negation, Transitivity: Simple average over conditions", adj=0, cex=.7, col="grey30")
    })

plot2 <- xyplot(
  1~1, type="n", xlim=c(.8, 2.2), ylim=c(0,1),
  ylab=" ", xlab="", xlab.top="Genre\n",
  par.settings=my_settings, axis=axis_L,
  scales=list(x=list(at=c(1,2), label=c("Fiction", "Non")),
              y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
  panel=function(x,y){
    panel.points(y=plogis(deceive_effect_genre$fit), 
                 x=1:2, type="l", col=1)
    panel.points(y=plogis(deceive_effect_genre$fit), 
                 x=1:2, type="p", col=1, pch=19, cex=.4)
    
    panel.points(y=plogis(delude_effect_genre$fit), 
                 x=1:2-c(.05, .05), type="l", col=1)
    panel.points(y=plogis(delude_effect_genre$fit), 
                 x=1:2-c(.05, .05), type="p", col=1, pch=19, cex=.4)
    
    panel.points(y=plogis(fool_effect_genre$fit), 
                 x=1:2, type="l", col=1)
    panel.points(y=plogis(fool_effect_genre$fit),
                 x=1:2, type="p", col=1, pch=19, cex=.4)
    
    panel.segments(x0=1:2, x1=1:2, 
                   y0=plogis(deceive_effect_genre$upper), 
                   y1=plogis(deceive_effect_genre$lower))
    panel.segments(x0=1:2-c(.05, .05), x1=1:2-c(.05, .05), 
                   y0=plogis(delude_effect_genre$upper), 
                   y1=plogis(delude_effect_genre$lower))
    panel.segments(x0=1:2, x1=1:2, 
                   y0=plogis(fool_effect_genre$upper),
                   y1=plogis(fool_effect_genre$lower))
    
    panel.text(x=2.1, y=plogis(c(deceive_effect_genre$fit[2], 
                                 delude_effect_genre$fit[2], 
                                 fool_effect_genre$fit[2])),
               label=c("deceive", "delude", "fool"), cex=.8, font=3, adj=0)
    })


plot3 <- xyplot(
  1~1, type="n", xlim=c(.8, 2.2), ylim=c(0,1),
  ylab=" ", xlab="", xlab.top="Negation\n",
  par.settings=my_settings, axis=axis_L,
  scales=list(x=list(at=c(1,2), label=c("No", "Yes")),
              y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
  panel=function(x,y){
    panel.points(y=plogis(deceive_effect_negation$fit), 
                 x=1:2, type="l", col=1)
    panel.points(y=plogis(deceive_effect_negation$fit), 
                 x=1:2, type="p", col=1, pch=19, cex=.4)
    
    panel.points(y=plogis(delude_effect_negation$fit), 
                 x=1:2-c(.05, .05), type="l", col=1)
    panel.points(y=plogis(delude_effect_negation$fit), 
                 x=1:2-c(.05, .05), type="p", col=1, pch=19, cex=.4)
    
    panel.points(y=plogis(fool_effect_negation$fit), 
                 x=1:2, type="l", col=1)
    panel.points(y=plogis(fool_effect_negation$fit), 
                 x=1:2, type="p", col=1, pch=19, cex=.4)
    
    panel.segments(x0=1:2, x1=1:2, 
                   y0=plogis(deceive_effect_negation$upper), 
                   y1=plogis(deceive_effect_negation$lower))
    panel.segments(x0=1:2-c(.05, .05), x1=1:2-c(.05, .05), 
                   y0=plogis(delude_effect_negation$upper), 
                   y1=plogis(delude_effect_negation$lower))
    panel.segments(x0=1:2, x1=1:2,
                   y0=plogis(fool_effect_negation$upper), 
                   y1=plogis(fool_effect_negation$lower))

    panel.text(x=2.1, y=plogis(c(deceive_effect_negation$fit[2],
                                 delude_effect_negation$fit[2], 
                                 fool_effect_negation$fit[2])),
               label=c("deceive", "delude", "fool"), cex=.8, font=3, adj=0)
    })


plot4 <- xyplot(
  1~1, type="n", xlim=c(.8, 3.2), ylim=c(0,1),
  ylab=" ", xlab="", xlab.top="Transitivity\n",
  par.settings=my_settings, axis=axis_L,
  scales=list(x=list(at=c(1,2,3), label=c("Pass", "Refl", "Trans")),
              y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
  panel=function(x,y){
    panel.points(y=plogis(deceive_effect_transitivity$fit), 
                 x=1:3, type="l", col=1)
    panel.points(y=plogis(deceive_effect_transitivity$fit), 
                 x=1:3, type="p", col=1, pch=19, cex=.4)
    
    panel.points(y=plogis(delude_effect_transitivity$fit), 
                 x=1:3-c(.05, .05, .05), type="l", col=1)
    panel.points(y=plogis(delude_effect_transitivity$fit), 
                 x=1:3-c(.05, .05, .05), type="p", col=1, pch=19, cex=.4)
    
    panel.points(y=plogis(fool_effect_transitivity$fit), 
                 x=1:3, type="l", col=1)
    panel.points(y=plogis(fool_effect_transitivity$fit), 
                 x=1:3, type="p", col=1, pch=19, cex=.4)
    
    panel.segments(x0=1:3, x1=1:3,
                   y0=plogis(deceive_effect_transitivity$upper), 
                   y1=plogis(deceive_effect_transitivity$lower))
    panel.segments(x0=1:3-c(.05, .05, .05), x1=1:3-c(.05, .05),
                   y0=plogis(delude_effect_transitivity$upper), 
                   y1=plogis(delude_effect_transitivity$lower))
    panel.segments(x0=1:3, x1=1:3, y0=plogis(fool_effect_transitivity$upper), 
                   y1=plogis(fool_effect_transitivity$lower))
    
    panel.text(x=3.1, y=plogis(c(deceive_effect_transitivity$fit[3], 
                                 delude_effect_transitivity$fit[3], 
                                 fool_effect_transitivity$fit[3])),
               label=c("deceive", "delude", "fool"), cex=.8, font=3, adj=0)
    })


print(plot1, position=c(0,0,.33,1), more=T)
print(plot2, position=c(.35,0,.53,1), more=T)
print(plot3, position=c(.55,0,.73,1), more=T)
print(plot4, position=c(.75,0,.95,1))


cairo_pdf("./figures/summary_midterm.pdf", width=7.5, height=2.5)
print(plot1, position=c(0,0,.33,1), more=T)
print(plot2, position=c(.35,0,.53,1), more=T)
print(plot3, position=c(.55,0,.73,1), more=T)
print(plot4, position=c(.75,0,.95,1))
dev.off()

```