---
title: "Short-term diachronic perspective: Loss of interpretators, AmE only"
output: html_document
---


```{r}
library(tidyverse)
library(effects)
library(lattice)
library(latticeExtra)
library(vcd)
library(car)
library(arm)

source("./r_utils/my_utils.R")

all_data <- read.csv("./data/all_data.csv", stringsAsFactors = T)
all_data$transitivity <- factor(all_data$transitivity, levels=c("transitive", "reflexive", "passive"))
contrasts(all_data$variety) <- contr.sum(2)
contrasts(all_data$transitivity) <- contr.sum(3)
contrasts(all_data$negation) <- contr.sum(2)

all_data$macro_genre <- factor(all_data$macro_genre, levels=levels(all_data$macro_genre)[c(3,1,2)], ordered=T)

contrasts(all_data$macro_genre) <- contr.sum(3)
data_short_AmE <- subset(all_data, year >= 1975 & variety=="AmE")
```


# Deceive

## Data
```{r}
data_short_AmE_deceive <- subset(data_short_AmE, verb == "deceive")
rownames(data_short_AmE_deceive) <- 1:nrow(data_short_AmE_deceive)
```

## Data inspection
```{r}
structable(variety + macro_genre + negation ~ transitivity, data_short_AmE_deceive)
```

```{r fig.height=3, fig.width=3}
data_short_AmE_deceive %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=1) +  
  facet_grid(rows=vars(macro_genre)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") + xlim(1975, 2020) +
  labs(title="Deceive",
       subtitle="Cases by Year and Genre")
```




## Model 
```{r}
m_short_deceive <- glm(
  interpretator_present ~ year_c + macro_genre + transitivity + negation, 
  data=data_short_AmE_deceive, family="binomial")

display(m_short_deceive)
```


## Model checking

Residual plots
```{r fig.height=3, fig.width=12}
residualPlots(m_short_deceive, layout=c(1,6), tests = F, ask=F)
```

Marginal model plots
```{r fig.height=3, fig.width=5, warning=F}
marginalModelPlots(m_short_deceive, layout=c(1,2))
```

Influence diagnostics
```{r fig.height=4, fig.width=4}
outlier_id <- influencePlot(m_short_deceive)
```

Effect of influential cases on coefficients + SEs
```{r}
outlier_id <- as.integer(rownames(outlier_id))

m_short_deceive_1 <- update(m_short_deceive, subset=-outlier_id[1])
m_short_deceive_2 <- update(m_short_deceive, subset=-outlier_id[2])
m_short_deceive_3 <- update(m_short_deceive, subset=-outlier_id[3])
m_short_deceive_4 <- update(m_short_deceive, subset=-outlier_id[4])
m_short_deceive_5 <- update(m_short_deceive, subset=-outlier_id)

coef_change <- compareCoefs(
  m_short_deceive, 
  m_short_deceive_1,
  m_short_deceive_2, 
  m_short_deceive_3,
  m_short_deceive_4,
  m_short_deceive_5,digits=2)
```

```{r}
data_short_AmE_deceive[outlier_id,]
```


## Model visualization

```{r fig.width=10, fig.height=3}
plot(effects::predictorEffect(
  "year_c",
  m_short_deceive, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    macro_genre1 = 0,
    macro_genre2 = 0,
    transitivity1 = 0,
    transitivity2 = 0,
    negation1 = 0))), 
  axes=list(y=list(type="response", lim=c(0,1))),
  lattice=list(array=list(row=1, col=1, nrow=1, ncol=4, more=T)),
  main="Year", xlab="")

plot(effects::predictorEffect(
  "macro_genre",
  m_short_deceive, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    year_c = 0,
    transitivity1 = 0,
    transitivity2 = 0,
    negation1 = 0))), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=2, nrow=1, ncol=4, more=T)),
  main="Genre", xlab="", ylab="")

plot(effects::predictorEffect(
  "negation",
  m_short_deceive, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    macro_genre1 = 0,
    macro_genre2 = 0,
    transitivity1 = 0,
    transitivity2 = 0,
    year_c = 0))), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=3, nrow=1, ncol=4, more=T)),
  main="Negation", xlab="", ylab="")

plot(effects::predictorEffect(
  "transitivity",
  m_short_deceive, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    macro_genre1 = 0,
    macro_genre2 = 0,
    year_c = 0,
    negation1 = 0))), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=4, nrow=1, ncol=4, more=T)),
  main="Transitivity", xlab="", ylab="")
```










# Delude

## Data
```{r}
data_short_AmE_delude <- subset(data_short_AmE, verb == "delude")
rownames(data_short_AmE_delude) <- 1:nrow(data_short_AmE_delude)
```

## Data inspection
```{r}
structable(variety + macro_genre + negation ~ transitivity, data_short_AmE_delude)
```


```{r fig.height=3, fig.width=3}
data_short_AmE_delude %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=1) +  
  facet_grid(rows=vars(macro_genre)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") + xlim(1975, 2020) +
  labs(title="Delude",
       subtitle="Cases by Year and Genre")
```

## Model 
```{r}
m_short_delude <- glm(
  interpretator_present ~ year_c + macro_genre + transitivity + negation, 
  data=data_short_AmE_delude, family="binomial")

display(m_short_delude)
```

## Model checking

Residual plots
```{r fig.height=2.5, fig.width=12}
residualPlots(m_short_delude, layout=c(1,6), tests = F, ask=F)
```

Marginal model plots
```{r fig.height=3, fig.width=5, warning=F}
marginalModelPlots(m_short_delude, layout=c(1,2))
```

Influence diagnostics
```{r fig.height=4, fig.width=4}
outlier_id <- influencePlot(m_short_delude)
```

Effect of influential cases on coefficients + SEs
```{r}
outlier_id <- as.integer(rownames(outlier_id))

m_short_delude_1 <- update(m_short_delude, subset=-outlier_id[1])
m_short_delude_2 <- update(m_short_delude, subset=-outlier_id[2])
m_short_delude_3 <- update(m_short_delude, subset=-outlier_id[3])
m_short_delude_4 <- update(m_short_delude, subset=-outlier_id[4])
m_short_delude_5 <- update(m_short_delude, subset=-outlier_id[5])
m_short_delude_6 <- update(m_short_delude, subset=-outlier_id)

coef_change <- compareCoefs(
  m_short_delude, 
  m_short_delude_1,
  m_short_delude_2, 
  m_short_delude_3,
  m_short_delude_4,
  m_short_delude_5,
  m_short_delude_6, digits=2)
```

```{r}
data_short_AmE_delude[outlier_id,]
```

## Model visualization


```{r fig.width=10, fig.height=3}
plot(effects::predictorEffect(
  "year_c",
  m_short_delude, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    macro_genre1 = 0,
    macro_genre2 = 0,
    transitivity1 = 0,
    transitivity2 = 0,
    negation1 = 0))), 
  axes=list(y=list(type="response", lim=c(0,1))),
  lattice=list(array=list(row=1, col=1, nrow=1, ncol=4, more=T)),
  main="Year", xlab="")

plot(effects::predictorEffect(
  "macro_genre",
  m_short_delude, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    year_c = 0,
    transitivity1 = 0,
    transitivity2 = 0,
    negation1 = 0))), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=2, nrow=1, ncol=4, more=T)),
  main="Genre", xlab="", ylab="")

plot(effects::predictorEffect(
  "negation",
  m_short_delude, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    macro_genre1 = 0,
    macro_genre2 = 0,
    transitivity1 = 0,
    transitivity2 = 0,
    year_c = 0))), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=3, nrow=1, ncol=4, more=T)),
  main="Negation", xlab="", ylab="")

plot(effects::predictorEffect(
  "transitivity",
  m_short_delude, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    macro_genre1 = 0,
    macro_genre2 = 0,
    year_c = 0,
    negation1 = 0))), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=4, nrow=1, ncol=4, more=T)),
  main="Transitivity", xlab="", ylab="")
```










# Fool

## Data
```{r}
data_short_AmE_fool <- subset(data_short_AmE, verb == "fool")
rownames(data_short_AmE_fool) <- 1:nrow(data_short_AmE_fool)
```

## Data inspection
```{r}
structable(variety + macro_genre + negation ~ transitivity, data_short_AmE_fool)
```

```{r fig.height=3, fig.width=3}
data_short_AmE_fool %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=1) +  
  facet_grid(rows=vars(macro_genre)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") + xlim(1975, 2020) +
  labs(title="Fool",
       subtitle="Cases by Year and Genre")
```

## Model 
```{r}
m_short_fool <- glm(
  interpretator_present ~ year_c + macro_genre + transitivity + negation, 
  data=data_short_AmE_fool, family="binomial")

display(m_short_fool)
```

## Model checking

Residual plots
```{r fig.height=2.5, fig.width=12}
residualPlots(m_short_fool, layout=c(1,6), tests = F, ask=F)
```

Marginal model plots
```{r fig.height=3, fig.width=5, warning=F}
marginalModelPlots(m_short_fool, layout=c(1,2))
```

Influence diagnostics
```{r fig.height=4, fig.width=4}
outlier_id <-influencePlot(m_short_fool)
```

Effect of influential cases on coefficients + SEs
```{r}
outlier_id <- as.integer(rownames(outlier_id))

m_short_fool_1 <- update(m_short_fool, subset=-outlier_id[1])
m_short_fool_2 <- update(m_short_fool, subset=-outlier_id[2])
m_short_fool_3 <- update(m_short_fool, subset=-outlier_id[3])
m_short_fool_4 <- update(m_short_fool, subset=-outlier_id[4])
m_short_fool_5 <- update(m_short_fool, subset=-outlier_id[5])
m_short_fool_all <- update(m_short_fool, subset=-outlier_id)

coef_change <-compareCoefs(
  m_short_fool, 
  m_short_fool_1,
  m_short_fool_2, 
  m_short_fool_3,
  m_short_fool_4,
  m_short_fool_5,
  m_short_fool_all, digits=2)
```


```{r}
data_short_AmE_fool[outlier_id,]
```

## Model visualization


```{r fig.width=10, fig.height=3}
plot(effects::predictorEffect(
  "year_c",
  m_short_fool, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    macro_genre1 = 0,
    macro_genre2 = 0,
    transitivity1 = 0,
    transitivity2 = 0,
    negation1 = 0))), 
  axes=list(y=list(type="response", lim=c(0,1))),
  lattice=list(array=list(row=1, col=1, nrow=1, ncol=4, more=T)),
  main="Year", xlab="")

plot(effects::predictorEffect(
  "macro_genre",
  m_short_fool, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    year_c = 0,
    transitivity1 = 0,
    transitivity2 = 0,
    negation1 = 0))), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=2, nrow=1, ncol=4, more=T)),
  main="Genre", xlab="", ylab="")

plot(effects::predictorEffect(
  "negation",
  m_short_fool, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    macro_genre1 = 0,
    macro_genre2 = 0,
    transitivity1 = 0,
    transitivity2 = 0,
    year_c = 0))), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=3, nrow=1, ncol=4, more=T)),
  main="Negation", xlab="", ylab="")

plot(effects::predictorEffect(
  "transitivity",
  m_short_fool, 
  confidence.level=.95,
  fixed.predictors=list(given.values=c(
    macro_genre1 = 0,
    macro_genre2 = 0,
    year_c = 0,
    negation1 = 0))), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=4, nrow=1, ncol=4, more=T)),
  main="Transitivity", xlab="", ylab="")
```


