---
title: "Untitled"
output: html_document
---

loss of complementizers

all data
3 models (per interpretator type: nominal, verbal, none)
random effects: verb
factors: variety, year
outcome: complementizer (y vs. n)

```{r}
source("./r_utils/my_utils.R")

library(vcd)
library(tidyverse)
library(lme4)
library(arm)
library(car)
library(effects)

all_data <- read.csv("./data/all_data.csv", stringsAsFactors = T)


all_data$transitivity <- factor(all_data$transitivity, levels=c("transitive", "reflexive", "passive"))


all_data$genre_binary <- factor(ifelse(all_data$macro_genre=="spoken", "fiction", as.character(all_data$macro_genre)))
all_data$genre_binary <- factor(ifelse(all_data$genre_binary=="fiction", "fiction", "non"), levels=c("non", "fiction"))

contrasts(all_data$variety) <- contr.sum(2)
contrasts(all_data$verb) <- contr.sum(3)
contrasts(all_data$transitivity) <- contr.sum(3)
contrasts(all_data$negation) <- contr.sum(2)
contrasts(all_data$genre_binary) <- contr.sum(2)


str(all_data)
```

```{r}
all_data <- subset(all_data, complementizer=="y" | complementizer=="n")
all_data$complementizer <- droplevels(all_data$complementizer)

all_data$complementizer_present <- ifelse(all_data$complementizer=="y", 1, 0)
table(all_data$complementizer)
```

```{r}
table(all_data$interpretator_type)
```

# Verbal


## Data

```{r}
comp_verbal <- subset(all_data, interpretator_type=="verbal")
rownames(comp_verbal) <- 1:nrow(comp_verbal)
#comp_verbal <- droplevels(comp_verbal)
str(comp_verbal)
```

```{r}
structable(variety ~ year_bins_40, comp_verbal)
```

```{r fig.height=3, fig.width=4.5}
comp_verbal %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=4) +
  facet_grid(rows=vars(variety)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") +
  labs(title="Verbal",
       subtitle="Cases by Year and Variety")
```

```{r fig.height=3, fig.width=4.5}
comp_verbal %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=4) +
  facet_grid(rows=vars(verb)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") +
  labs(title="Verbal",
       subtitle="Cases by Year and Verb")
```

```{r}
m_comp_verbal <- glm(complementizer_present ~ year_c + variety + verb,
                     data=comp_verbal, family="binomial")

display(m_comp_verbal)
```

```{r fig.width=6, fig.height=6}
plot(allEffects(m_comp_verbal), type="response", ylim=c(0,1))
```

```{r fig.width=8, fig.height=3}
plot(effects::predictorEffect(
  "year_c",
  m_comp_verbal, 
  confidence.level=.95), 
  axes=list(y=list(type="response", lim=c(0,1))),
  lattice=list(array=list(row=1, col=1, nrow=1, ncol=3, more=T)),
  main="Year", xlab="")

plot(effects::predictorEffect(
  "variety",
  m_comp_verbal, 
  confidence.level=.95), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=2, nrow=1, ncol=3, more=T)),
  main="Variety", xlab="", ylab="")

plot(effects::predictorEffect(
  "verb",
  m_comp_verbal, 
  confidence.level=.95), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=3, nrow=1, ncol=3, more=F)),
  main="Verb", xlab="", ylab="")
```


## Model checking

Residual plots
```{r fig.height=3, fig.width=7}
car::residualPlots(m_comp_verbal, layout=c(1,4), tests = F, ask=F)
```

Marginal model plots
```{r fig.height=3.5, fig.width=6, warning=F}
car::marginalModelPlots(m_comp_verbal, layout=c(1,2), ylim=c(0,1))
```

Influence diagnostics
```{r fig.height=5, fig.width=5}
car::influencePlot(m_comp_verbal)
```

```{r}
comp_verbal[c(1483, 1747, 1748, 1749),]
```


Effect of influential cases on coefficients + SEs
```{r}
m_comp_verbal_1 <- update(m_comp_verbal, subset=-1483)
m_comp_verbal_2 <- update(m_comp_verbal, subset=-1747)
m_comp_verbal_3 <- update(m_comp_verbal, subset=-1748)
m_comp_verbal_4 <- update(m_comp_verbal, subset=-1749)
m_comp_verbal_all <- update(m_comp_verbal, subset=-c(1483, 1747, 1748, 1749))

car::compareCoefs(m_comp_verbal, 
                  m_comp_verbal_1,
                  m_comp_verbal_2, 
                  m_comp_verbal_3,
                  m_comp_verbal_4,
                  m_comp_verbal_all, digits=1)
```





# Nominal


## Data

```{r}
comp_nominal <- subset(all_data, interpretator_type=="nominal")
rownames(comp_nominal) <- 1:nrow(comp_nominal)
#comp_nominal <- droplevels(comp_nominal)
```

```{r}
structable(variety ~ year_bins_40, comp_nominal)
```

```{r fig.height=3, fig.width=4.5}
comp_nominal %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=4) +
  facet_grid(rows=vars(variety)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") +
  labs(title="nominal",
       subtitle="Cases by Year and Variety")
```

```{r fig.height=3, fig.width=4.5}
comp_nominal %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=4) +
  facet_grid(rows=vars(verb)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") +
  labs(title="nominal",
       subtitle="Cases by Year and Verb")
```

```{r}
m_comp_nominal <- glm(complementizer_present ~ year_c + variety + verb,
                     data=comp_nominal, family="binomial")

display(m_comp_nominal)
```

```{r fig.width=6, fig.height=6}
plot(allEffects(m_comp_nominal), type="response", ylim=c(0,1))
```


```{r fig.width=8, fig.height=3}
plot(effects::predictorEffect(
  "year_c",
  m_comp_nominal, 
  confidence.level=.95), 
  axes=list(y=list(type="response", lim=c(0,1))),
  lattice=list(array=list(row=1, col=1, nrow=1, ncol=3, more=T)),
  main="Year", xlab="")

plot(effects::predictorEffect(
  "variety",
  m_comp_nominal, 
  confidence.level=.95), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=2, nrow=1, ncol=3, more=T)),
  main="Variety", xlab="", ylab="")

plot(effects::predictorEffect(
  "verb",
  m_comp_nominal, 
  confidence.level=.95), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=3, nrow=1, ncol=3, more=F)),
  main="Verb", xlab="", ylab="")
```


## Model checking

Residual plots
```{r fig.height=3, fig.width=7}
car::residualPlots(m_comp_nominal, layout=c(1,4), tests = F, ask=F)
```

Marginal model plots
```{r fig.height=3.5, fig.width=6, warning=F}
car::marginalModelPlots(m_comp_nominal, layout=c(1,2), ylim=c(0,1))
```

Influence diagnostics
```{r fig.height=5, fig.width=5}
tmp <- influencePlot(m_comp_nominal)
influencePlot(m_comp_nominal)
```

```{r}
comp_nominal[rownames(tmp),]
```


Effect of influential cases on coefficients + SEs
```{r}
m_comp_nominal_1 <- update(m_comp_nominal, subset=-23)
m_comp_nominal_2 <- update(m_comp_nominal, subset=-65)
m_comp_nominal_3 <- update(m_comp_nominal, subset=-179)
m_comp_nominal_4 <- update(m_comp_nominal, subset=-330)
m_comp_nominal_all <- update(m_comp_nominal, subset=-c(23, 65, 179, 330))

car::compareCoefs(m_comp_nominal, 
                  m_comp_nominal_1,
                  m_comp_nominal_2, 
                  m_comp_nominal_3,
                  m_comp_nominal_4,
                  m_comp_nominal_all, digits=2)
```

# None


## Data

```{r}
comp_none <- subset(all_data, interpretator_type=="none")
rownames(comp_none) <- 1:nrow(comp_none)
#comp_none <- droplevels(comp_none)
```

```{r}
structable(variety ~ year_bins_40, comp_none)
```

```{r fig.height=3, fig.width=4.5}
comp_none %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=4) +
  facet_grid(rows=vars(variety)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") +
  labs(title="None",
       subtitle="Cases by Year and Variety")
```

```{r fig.height=3, fig.width=4.5}
comp_none %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=4) +
  facet_grid(rows=vars(verb)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") +
  labs(title="None",
       subtitle="Cases by Year and Verb")
```

```{r}
str(comp_none)
m_comp_none <- glm(complementizer_present ~ year_c + variety + verb,
                     data=comp_none, family="binomial")

display(m_comp_none)


```

```{r fig.width=8, fig.height=3}
plot(effects::predictorEffect(
  "year_c",
  m_comp_none, 
  confidence.level=.95), 
  axes=list(y=list(type="response", lim=c(0,1))),
  lattice=list(array=list(row=1, col=1, nrow=1, ncol=3, more=T)),
  main="Year", xlab="")

plot(effects::predictorEffect(
  "variety",
  m_comp_none, 
  confidence.level=.95), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=2, nrow=1, ncol=3, more=T)),
  main="Variety", xlab="", ylab="")

plot(effects::predictorEffect(
  "verb",
  m_comp_none, 
  confidence.level=.95), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=3, nrow=1, ncol=3, more=F)),
  main="Verb", xlab="", ylab="")
```


## Model checking

Residual plots
```{r fig.height=3, fig.width=7}
car::residualPlots(m_comp_none, layout=c(1,4), tests = F, ask=F)
```

Marginal model plots
```{r fig.height=3.5, fig.width=6, warning=F}
car::marginalModelPlots(m_comp_none, layout=c(1,2), ylim=c(0,1))
```

Influence diagnostics
```{r fig.height=5, fig.width=5}
tmp <- influencePlot(m_comp_none)
influencePlot(m_comp_none)
```

```{r}
comp_none[rownames(tmp),]
```


Effect of influential cases on coefficients + SEs
```{r}
m_comp_none_1 <- update(m_comp_none, subset=-23)
m_comp_none_2 <- update(m_comp_none, subset=-65)
m_comp_none_3 <- update(m_comp_none, subset=-179)
m_comp_none_4 <- update(m_comp_none, subset=-330)
m_comp_none_all <- update(m_comp_none, subset=-c(23, 65, 179, 330))

car::compareCoefs(m_comp_none, 
                  m_comp_none_1,
                  m_comp_none_2, 
                  m_comp_none_3,
                  m_comp_none_4,
                  m_comp_none_all, digits=2)
```


