---
title: "Untitled"
output: html_document
---

loss of complementizers

all data
3 models (per interpretator type: nominal, verbal, none)
random effects: verb
factors: variety, year
outcome: complementizer (y vs. n)

```{r}
source("./r_utils/my_utils.R")

library(vcd)
library(tidyverse)
library(lme4)
library(arm)
library(car)
library(effects)
library(lattice)

all_data <- read.csv("./data/all_data.csv", stringsAsFactors = T)


all_data$transitivity <- factor(all_data$transitivity, levels=c("transitive", "reflexive", "passive"))


all_data$genre_binary <- factor(ifelse(all_data$macro_genre=="spoken", "fiction", as.character(all_data$macro_genre)))
all_data$genre_binary <- factor(ifelse(all_data$genre_binary=="fiction", "fiction", "non"), levels=c("non", "fiction"))

contrasts(all_data$variety) <- contr.sum(2)
contrasts(all_data$verb) <- contr.sum(3)
contrasts(all_data$transitivity) <- contr.sum(3)
contrasts(all_data$negation) <- contr.sum(2)
contrasts(all_data$genre_binary) <- contr.sum(2)


str(all_data)
```

```{r}
all_data <- subset(all_data, complementizer=="y" | complementizer=="n")
all_data$complementizer <- droplevels(all_data$complementizer)

all_data$complementizer_present <- ifelse(all_data$complementizer=="y", 1, 0)
table(all_data$complementizer)
```

```{r}
table(all_data$interpretator_type)
```

# Verbal


## Data

```{r}
comp_verbal <- subset(all_data, interpretator_type=="verbal")
rownames(comp_verbal) <- 1:nrow(comp_verbal)
#comp_verbal <- droplevels(comp_verbal)
str(comp_verbal)
```

```{r}
structable(variety ~ year_bins_40, comp_verbal)
```

```{r fig.height=3, fig.width=4.5}
comp_verbal %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=4) +
  facet_grid(rows=vars(variety)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") +
  labs(title="Verbal",
       subtitle="Cases by Year and Variety")
```

```{r fig.height=3, fig.width=4.5}
comp_verbal %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=4) +
  facet_grid(rows=vars(verb)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") +
  labs(title="Verbal",
       subtitle="Cases by Year and Verb")
```

```{r}
str(comp_verbal)
m_comp_verbal <- glm(complementizer_present ~ year_c + variety + negation + genre_binary,
                     data=comp_verbal, family="binomial")

display(m_comp_verbal)
```


```{r fig.width=8, fig.height=3}
plot(effects::predictorEffect(
  "year_c",
  m_comp_verbal, 
  confidence.level=.95), 
  axes=list(y=list(type="response", lim=c(0,1))),
  lattice=list(array=list(row=1, col=1, nrow=1, ncol=4, more=T)),
  main="Year", xlab="")

plot(effects::predictorEffect(
  "variety",
  m_comp_verbal, 
  confidence.level=.95), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=2, nrow=1, ncol=4, more=T)),
  main="Variety", xlab="", ylab="")

plot(effects::predictorEffect(
  "negation",
  m_comp_verbal, 
  confidence.level=.95), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=3, nrow=1, ncol=4, more=T)),
  main="Negation", xlab="", ylab="")

plot(effects::predictorEffect(
  "genre_binary",
  m_comp_verbal, 
  confidence.level=.95), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=4, nrow=1, ncol=4, more=F)),
  main="Genre", xlab="", ylab="")
```


## Model checking

Residual plots
```{r fig.height=3, fig.width=7}
car::residualPlots(m_comp_verbal, layout=c(1,4), tests = F, ask=F)
```

Marginal model plots
```{r fig.height=3.5, fig.width=6, warning=F}
car::marginalModelPlots(m_comp_verbal, layout=c(1,2), ylim=c(0,1))
```

Influence diagnostics
```{r fig.height=5, fig.width=5}
car::influencePlot(m_comp_verbal)
```

```{r}
comp_verbal[c(1483, 1747, 1748, 1749),]
```


Effect of influential cases on coefficients + SEs
```{r}
m_comp_verbal_1 <- update(m_comp_verbal, subset=-1483)
m_comp_verbal_2 <- update(m_comp_verbal, subset=-1747)
m_comp_verbal_3 <- update(m_comp_verbal, subset=-1748)
m_comp_verbal_4 <- update(m_comp_verbal, subset=-1749)
m_comp_verbal_all <- update(m_comp_verbal, subset=-c(1483, 1747, 1748, 1749))

car::compareCoefs(m_comp_verbal, 
                  m_comp_verbal_1,
                  m_comp_verbal_2, 
                  m_comp_verbal_3,
                  m_comp_verbal_4,
                  m_comp_verbal_all, digits=1)
```


# Extract effects

```{r}
verbal_effect_year <- effect(
  "year_c",  m_comp_verbal, confidence.level=.95,
  xlevels=list(
    year_c=seq(min(comp_verbal$year_c), 
               max(comp_verbal$year_c), 
               length.out=50)),
  fixed.predictors=list(given.values=c(
    variety1 = 0,
    genre_binary1 = 0,
    negation1 = 0)))

verbal_effect_variety <- effect(
  "variety",  m_comp_verbal, confidence.level=.95,
  fixed.predictors=list(given.values=c(
    year_c = 0,
    genre_binary1 = 0,
    negation1 = 0)))

verbal_effect_genre <- effect(
  "genre_binary",  m_comp_verbal, confidence.level=.95,
  fixed.predictors=list(given.values=c(
    variety1 = 0,
    year_c = 0,
    negation1 = 0)))

verbal_effect_negation <- effect(
  "negation",  m_comp_verbal, confidence.level=.95,
  fixed.predictors=list(given.values=c(
    variety1 = 0,
    genre_binary1 = 0,
    year_c = 0)))
```




# Nominal


## Data

```{r}
comp_nominal <- subset(all_data, interpretator_type=="nominal")
rownames(comp_nominal) <- 1:nrow(comp_nominal)
#comp_nominal <- droplevels(comp_nominal)
```

```{r}
structable(variety ~ year_bins_40, comp_nominal)
```

```{r fig.height=3, fig.width=4.5}
comp_nominal %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=4) +
  facet_grid(rows=vars(variety)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") +
  labs(title="nominal",
       subtitle="Cases by Year and Variety")
```

```{r fig.height=3, fig.width=4.5}
comp_nominal %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=4) +
  facet_grid(rows=vars(verb)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") +
  labs(title="nominal",
       subtitle="Cases by Year and Verb")
```

```{r}
m_comp_nominal <- glm(complementizer_present ~ year_c + variety + negation + genre_binary,
                     data=comp_nominal, family="binomial")

display(m_comp_nominal)
```


```{r fig.width=8, fig.height=3}
plot(effects::predictorEffect(
  "year_c",
  m_comp_nominal, 
  confidence.level=.95), 
  axes=list(y=list(type="response", lim=c(0,1))),
  lattice=list(array=list(row=1, col=1, nrow=1, ncol=4, more=T)),
  main="Year", xlab="")

plot(effects::predictorEffect(
  "variety",
  m_comp_nominal, 
  confidence.level=.95), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=2, nrow=1, ncol=4, more=T)),
  main="Variety", xlab="", ylab="")

plot(effects::predictorEffect(
  "negation",
  m_comp_nominal, 
  confidence.level=.95), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=3, nrow=1, ncol=4, more=T)),
  main="Negation", xlab="", ylab="")

plot(effects::predictorEffect(
  "genre_binary",
  m_comp_nominal, 
  confidence.level=.95), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=4, nrow=1, ncol=4, more=F)),
  main="Genre", xlab="", ylab="")
```


## Model checking

Residual plots
```{r fig.height=3, fig.width=7}
car::residualPlots(m_comp_nominal, layout=c(1,4), tests = F, ask=F)
```

Marginal model plots
```{r fig.height=3.5, fig.width=6, warning=F}
car::marginalModelPlots(m_comp_nominal, layout=c(1,2), ylim=c(0,1))
```

Influence diagnostics
```{r fig.height=5, fig.width=5}
tmp <- influencePlot(m_comp_nominal)
influencePlot(m_comp_nominal)
```

```{r}
comp_nominal[rownames(tmp),]
```


Effect of influential cases on coefficients + SEs
```{r}
m_comp_nominal_1 <- update(m_comp_nominal, subset=-23)
m_comp_nominal_2 <- update(m_comp_nominal, subset=-65)
m_comp_nominal_3 <- update(m_comp_nominal, subset=-179)
m_comp_nominal_4 <- update(m_comp_nominal, subset=-330)
m_comp_nominal_all <- update(m_comp_nominal, subset=-c(23, 65, 179, 330))

car::compareCoefs(m_comp_nominal, 
                  m_comp_nominal_1,
                  m_comp_nominal_2, 
                  m_comp_nominal_3,
                  m_comp_nominal_4,
                  m_comp_nominal_all, digits=2)
```

# None


## Data

```{r}
comp_none <- subset(all_data, interpretator_type=="none")
rownames(comp_none) <- 1:nrow(comp_none)
#comp_none <- droplevels(comp_none)
```

```{r}
structable(variety ~ year_bins_40, comp_none)
```

```{r fig.height=3, fig.width=4.5}
comp_none %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=4) +
  facet_grid(rows=vars(variety)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") +
  labs(title="None",
       subtitle="Cases by Year and Variety")
```

```{r fig.height=3, fig.width=4.5}
comp_none %>% ggplot(aes(x=year)) + geom_dotplot(binwidth=4) +
  facet_grid(rows=vars(verb)) + theme_light() + scale_y_continuous(breaks =NULL) +
  ylab(" ") + xlab(" ") +
  labs(title="None",
       subtitle="Cases by Year and Verb")
```

```{r}
str(comp_none)
m_comp_none <- glm(complementizer_present ~ year_c + variety + negation + genre_binary,
                     data=comp_none, family="binomial")

display(m_comp_none)


```

```{r fig.width=8, fig.height=6}
plot(allEffects(m_comp_none), type="response", ylim=c(0,1))
```


```{r fig.width=8, fig.height=3}
plot(effects::predictorEffect(
  "year_c",
  m_comp_none, 
  confidence.level=.95), 
  axes=list(y=list(type="response", lim=c(0,1))),
  lattice=list(array=list(row=1, col=1, nrow=1, ncol=4, more=T)),
  main="Year", xlab="")

plot(effects::predictorEffect(
  "variety",
  m_comp_none, 
  confidence.level=.95), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=2, nrow=1, ncol=4, more=T)),
  main="Variety", xlab="", ylab="")

plot(effects::predictorEffect(
  "negation",
  m_comp_none, 
  confidence.level=.95), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=3, nrow=1, ncol=4, more=T)),
  main="Negation", xlab="", ylab="")

plot(effects::predictorEffect(
  "genre_binary",
  m_comp_none, 
  confidence.level=.95), 
  axes=list(y=list(type="response",lim=c(0,1))),
  lattice=list(array=list(row=1, col=4, nrow=1, ncol=4, more=F)),
  main="Genre", xlab="", ylab="")
```


## Model checking

Residual plots
```{r fig.height=3, fig.width=7}
car::residualPlots(m_comp_none, layout=c(1,4), tests = F, ask=F)
```

Marginal model plots
```{r fig.height=3.5, fig.width=6, warning=F}
car::marginalModelPlots(m_comp_none, layout=c(1,2), ylim=c(0,1))
```

Influence diagnostics
```{r fig.height=5, fig.width=5}
tmp <- influencePlot(m_comp_none)
influencePlot(m_comp_none)
```

```{r}
comp_none[rownames(tmp),]
```


Effect of influential cases on coefficients + SEs
```{r}
m_comp_none_1 <- update(m_comp_none, subset=-23)
m_comp_none_2 <- update(m_comp_none, subset=-65)
m_comp_none_3 <- update(m_comp_none, subset=-179)
m_comp_none_4 <- update(m_comp_none, subset=-330)
m_comp_none_all <- update(m_comp_none, subset=-c(23, 65, 179, 330))

car::compareCoefs(m_comp_none, 
                  m_comp_none_1,
                  m_comp_none_2, 
                  m_comp_none_3,
                  m_comp_none_4,
                  m_comp_none_all, digits=2)
```

# Extract effects

```{r}
none_effect_year <- effect(
  "year_c",  m_comp_none, confidence.level=.95,
  xlevels=list(
    year_c=seq(min(comp_none$year_c), 
               max(comp_none$year_c), 
               length.out=50)),
  fixed.predictors=list(given.values=c(
    variety1 = 0,
    genre_binary1 = 0,
    negation1 = 0)))

none_effect_variety <- effect(
  "variety",  m_comp_none, confidence.level=.95,
  fixed.predictors=list(given.values=c(
    year_c = 0,
    genre_binary1 = 0,
    negation1 = 0)))

none_effect_genre <- effect(
  "genre_binary",  m_comp_none, confidence.level=.95,
  fixed.predictors=list(given.values=c(
    variety1 = 0,
    year_c = 0,
    negation1 = 0)))

none_effect_negation <- effect(
  "negation",  m_comp_none, confidence.level=.95,
  fixed.predictors=list(given.values=c(
    variety1 = 0,
    genre_binary1 = 0,
    year_c = 0)))
```




# Combined display

```{r fig.height=3, fig.width=8}
plot1 <- xyplot(1~1, type="n", xlim=c(-6,.5), ylim=c(0,1),
       ylab="Complementizer present (%)", xlab="", xlab.top="Verb\n",
       par.settings=my_settings, axis=axis_L,
       scales=list(x=list(at=c(-6,-4,-2, 0), label=c(1700, 1800, 1900, 2000)),
                   y=list(at=c(0, .5, 1), label=c(0, 50, 100))),
       panel=function(x,y){
         panel.polygon(y=plogis(c(verbal_effect_year$lower, rev(verbal_effect_year$upper))),
                       x=c(verbal_effect_year$x$year_c, rev(verbal_effect_year$x$year_c)),
                       border=F, col="grey", alpha=.3)
         panel.polygon(y=plogis(c(none_effect_year$lower, rev(none_effect_year$upper))),
                       x=c(none_effect_year$x$year_c, rev(none_effect_year$x$year_c)),
                       border=F, col="grey", alpha=.3)

         panel.points(y=plogis(verbal_effect_year$fit), x=verbal_effect_year$x$year_c, type="l", col=1, lty=3, lineend="square")
         panel.points(y=plogis(none_effect_year$fit), x=none_effect_year$x$year_c, type="l", col=1)

         panel.points(x=.5, y=.6, pch=16, col="white", cex=1.8)
         panel.text(x=c(.4, -.8), y=c(.75, .25), label=c("none", "verbal"), font=3, cex=.9)
         panel.text(x=-6, y=-.19, label="Adjusted to: Year = 2000; Variety/Genre/Negation: Simple average over conditions", adj=0, cex=.7, col="grey30")
         panel.text(x=-6, y=-.28, label="Error bars denote 95% uncertainty intervals", adj=0, cex=.7, col="grey30")
         panel.arrows(x0=0, x1=0, y0=.05, y1=.01, code=2, angle=10, length=.05, col="grey")
         })

plot2 <- xyplot(1~1, type="n", xlim=c(.8, 2.2), ylim=c(0,1),
       ylab="", xlab="", xlab.top="Variety\n",
       par.settings=my_settings, axis=axis_L,
       scales=list(x=list(at=c(1,2), label=c("AmE", "BrE")),
                   y=list(at=c(0, .5, 1), label=c("", "", ""))),
       panel=function(x,y){
         panel.segments(x0=c(1,2)+.025, x1=c(1,2)+.025, y0=plogis(none_effect_variety$upper), y1=plogis(none_effect_variety$lower))
         panel.segments(x0=c(1,2)-.025, x1=c(1,2)-.025, y0=plogis(verbal_effect_variety$upper), y1=plogis(verbal_effect_variety$lower))
         
         panel.points(x=c(1,2)+.025, y=plogis(none_effect_variety$fit), type="l", col=1)
         panel.points(x=c(1,2)+.025, y=plogis(none_effect_variety$fit), type="p", col=1, pch=19, cex=.4)
         
         panel.points(x=c(1,2)-.025, y=plogis(verbal_effect_variety$fit), type="l", col=1, lty=3, lineend="square")
         panel.points(x=c(1,2)-.025, y=plogis(verbal_effect_variety$fit), type="p", col=1, pch=21, fill="white", cex=.4)
         
         panel.text(x=2.1, y=plogis(c(none_effect_variety$fit[2],
                                      verbal_effect_variety$fit[2]))+c(.0,.01),
                    label=c("none", "verbal"), font=3, cex=.8, adj=0)
         })


plot3 <- xyplot(1~1, type="n", xlim=c(.8, 2.2), ylim=c(0,1),
       ylab="", xlab="", xlab.top="Genre\n",
       par.settings=my_settings, axis=axis_L,
       scales=list(x=list(at=c(1,2), label=c("Non", "Fiction")),
                   y=list(at=c(0, .5, 1), label=c("", "", ""))),
       panel=function(x,y){
         panel.segments(x0=c(1,2)+.025, x1=c(1,2)+.025, y0=plogis(none_effect_genre$upper), y1=plogis(none_effect_genre$lower))
         panel.segments(x0=c(1,2)-.025, x1=c(1,2)-.025, y0=plogis(verbal_effect_genre$upper), y1=plogis(verbal_effect_genre$lower))
         
         panel.points(x=c(1,2)+.025, y=plogis(none_effect_genre$fit), type="l", col=1)
         panel.points(x=c(1,2)+.025, y=plogis(none_effect_genre$fit), type="p", col=1, pch=19, cex=.4)
         
         panel.points(x=c(1,2)-.025, y=plogis(verbal_effect_genre$fit), type="l", col=1, lty=3, lineend="square")
         panel.points(x=c(1,2)-.025, y=plogis(verbal_effect_genre$fit), type="p", col=1, pch=21, fill="white", cex=.4)
         
         panel.text(x=2.1, y=plogis(c(none_effect_genre$fit[2],
                                      verbal_effect_genre$fit[2]))+c(.0,.01),
                    label=c("none", "verbal"), font=3, cex=.8, adj=0)
         })


plot4 <- xyplot(1~1, type="n", xlim=c(.8, 2.2), ylim=c(0,1),
       ylab="", xlab="", xlab.top="Negation\n",
       par.settings=my_settings, axis=axis_L,
       scales=list(x=list(at=c(1,2), label=c("No", "Yes")),
                   y=list(at=c(0, .5, 1), label=c("", "", ""))),
       panel=function(x,y){
         panel.segments(x0=c(1,2)+.025, x1=c(1,2)+.025, y0=plogis(none_effect_negation$upper), y1=plogis(none_effect_negation$lower))
         panel.segments(x0=c(1,2)-.025, x1=c(1,2)-.025, y0=plogis(verbal_effect_negation$upper), y1=plogis(verbal_effect_negation$lower))
         
         panel.points(x=c(1,2)+.025, y=plogis(none_effect_negation$fit), type="l", col=1)
         panel.points(x=c(1,2)+.025, y=plogis(none_effect_negation$fit), type="p", col=1, pch=19, cex=.4)
         
         panel.points(x=c(1,2)-.025, y=plogis(verbal_effect_negation$fit), type="l", col=1, lty=3, lineend="square")
         panel.points(x=c(1,2)-.025, y=plogis(verbal_effect_negation$fit), type="p", col=1, pch=21, fill="white", cex=.4)
         
         panel.text(x=2.1, y=plogis(c(none_effect_negation$fit[2],
                                      verbal_effect_negation$fit[2]))+c(.0,.01),
                    label=c("none", "verbal"), font=3, cex=.8, adj=0)
         })


print(plot1, position=c(0,0,.35,1), more=T)
print(plot2, position=c(.40,0,.55,1), more=T)
print(plot3, position=c(.60,0,.75,1), more=T)
print(plot4, position=c(.80,0,.95,1))

cairo_pdf("./figures/complementizers_summary.pdf", width=7, height=2.7)
print(plot1, position=c(0,.05,.35,1), more=T)
print(plot2, position=c(.40,.05,.55,1), more=T)
print(plot3, position=c(.60,.05,.75,1), more=T)
print(plot4, position=c(.80,.05,.95,1))
dev.off()
```