---
title: "Untitled"
output: html_document
---

R packages

```{r}
library(tidyverse)
library(lattice)
```

# Data screening

First we load the data, then select only *delude*:

```{r}
data_merged <- read.csv("./data/data_merged.csv", stringsAsFactors = T)

data_delude <- subset(data_merged, verb=="delude")
data_delude <- droplevels(data_delude)
str(data_delude)
```

Inspect different variables via contingency tables:

```{r}
xtabs(~variety, data=data_delude)
```


```{r}
xtabs(~corpus, data=data_delude)
```

```{r}
xtabs(~genre, data=data_delude)
```

```{r}
xtabs(~negation, data=data_delude)
```

```{r}
xtabs(~transitivity, data=data_delude)
```

For YEAR, we use a graph:

```{r fig.height=3, fig.width=3}
histogram(~year, data=data_delude)
```

# Synchronic data

Exclude COHA data:

```{r}
delude_syn <- subset(data_delude, corpus!="COHA")
delude_syn <- droplevels(delude_syn)
str(delude_syn)
```


Inspect different variables via contingency tables:

```{r}
xtabs(~variety, data=delude_syn)
```


```{r}
xtabs(~corpus, data=delude_syn)
```

```{r}
xtabs(~genre, data=delude_syn)
```

```{r}
xtabs(~negation, data=delude_syn)
```

```{r}
xtabs(~transitivity, data=delude_syn)
```

For YEAR, we use a graph:

```{r fig.height=3, fig.width=3}
histogram(delude_syn$year)
```

Break down YEAR by variety:

```{r fig.height=3, fig.width=5}
histogram(~year | variety, data=delude_syn)
```



## Cross-tabulations


TRANSITIVITY x NEGATION

```{r}
xtabs(~transitivity + negation, data=delude_syn)
```

```{r}
round(
  prop.table(
    xtabs(~ negation + transitivity, data=delude_syn), 
    margin = 2),
  2)
```

TRANSITIVITY x GENRE

```{r}
xtabs(~transitivity + genre, data=delude_syn)
```

```{r}
round(
  prop.table(
    xtabs(~transitivity + genre, data=delude_syn), 
    margin = 2),
  2)
```

NEGATION x GENRE

```{r}
xtabs(~negation + genre, data=delude_syn)
```

```{r}
round(
  prop.table(
    xtabs(~negation + genre, data=delude_syn), 
    margin = 2),
  2)
```


